---
title: "Experiment 3 Section 7/8 Replication: Trust and Interaction Experience Regression (No Baseline in Q1-Q3)"
output:
  html_document: default
  pdf_document: default
params:
  data_dirs:
    - "../data/0318/data"
    - "../data/0319/data"
    - "../data/0322/data"
  csv_pattern: "^user_.*\\.csv$"
  alpha: 0.05
  seed: 20260323
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(params$seed)
```

```{r table-spacing-style, results='asis', echo=FALSE}
table_column_padding_html <- "2rem"
table_column_padding_latex <- "10pt"

if (knitr::is_html_output()) {
  cat(
    "<style>\n",
    "table th,\n",
    "table td {\n",
    "  padding-left: ", table_column_padding_html, " !important;\n",
    "  padding-right: ", table_column_padding_html, " !important;\n",
    "}\n",
    "</style>\n",
    sep = ""
  )
}

if (knitr::is_latex_output()) {
  cat("\\setlength{\\tabcolsep}{", table_column_padding_latex, "}\n", sep = "")
}
```

## Goal

Replicate Experiment 3 notebook Section 7 and Section 8 analysis structure with two regression outcomes:

- `composite_trust_score ~ vis_type * interaction * detail_presentation + general_trust_composite + participant_id`
- `interaction_experience ~ vis_type * interaction * detail_presentation + participant_id`

This report follows the same trust-survey preprocessing used in `analysis-0318.ipynb`, including:

- loading `0318`, `0319`, `0322` batches
- extracting trust/interaction items from `response`
- normalizing Likert items from `0-6` to `1-7` when needed
- excluding attention-check failures

## Packages

```{r packages}
required_packages <- c(
  "dplyr",
  "jsonlite",
  "knitr",
  "emmeans",
  "ggplot2",
  "lme4",
  "lmerTest"
)

missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)
]

if (length(missing_packages) > 0) {
  stop(
    "Missing required packages: ",
    paste(missing_packages, collapse = ", "),
    ". Install them before rendering."
  )
}

lapply(required_packages, library, character.only = TRUE)
```

## Paths

```{r paths}
report_dir <- local({
  current_input <- tryCatch(
    knitr::current_input(),
    error = function(e) character(0)
  )

  if (length(current_input) == 1 && nzchar(current_input)) {
    input_path <- current_input

    if (!grepl("^(/|[A-Za-z]:[/\\\\])", input_path)) {
      input_path <- file.path(getwd(), input_path)
    }

    if (grepl("\\.[Rr]md$", input_path) || file.exists(input_path)) {
      return(normalizePath(dirname(input_path), winslash = "/", mustWork = TRUE))
    }
  }

  fallback_dir <- file.path(getwd(), "Experiment3", "analysis")
  normalizePath(fallback_dir, winslash = "/", mustWork = TRUE)
})

resolve_report_path <- function(path_value) {
  if (grepl("^(/|[A-Za-z]:[/\\\\])", path_value)) {
    return(normalizePath(path_value, winslash = "/", mustWork = TRUE))
  }

  normalizePath(
    file.path(report_dir, path_value),
    winslash = "/",
    mustWork = TRUE
  )
}

data_dirs <- vapply(params$data_dirs, resolve_report_path, character(1))
```

## Constants

```{r constants}
BASELINE_CONDITION_NUMBER <- 1
TREATMENT_CONDITIONS <- c(21, 22, 23, 24, 25, 26)

INTERACTION_CONDITION_LABELS <- c(
  "1" = "Baseline",
  "21" = "Hover Show One",
  "22" = "Hover Show All",
  "23" = "Click Show One",
  "24" = "Click Show All",
  "25" = "Animation Show One",
  "26" = "Animation Show All"
)

SECTION7_INTERACTION_ORDER <- c(
  "Hover Show One",
  "Hover Show All",
  "Click Show One",
  "Click Show All",
  "Animation Show One",
  "Animation Show All"
)

TRUST_ITEM_KEYS <- c(
  "skeptical_rating",
  "data_trust",
  "usability_difficulty",
  "comprehension_ease"
)

INTERACTION_ITEM_KEYS <- c(
  "navigation_control",
  "content_control",
  "pace_control",
  "interface_exploration",
  "interface_responsiveness",
  "user_communication",
  "personal_conversation",
  "interface_interaction",
  "interface_sensitivity"
)

PERSONALITY_ITEM_KEYS <- c(
  "respect_others",
  "good_word_everyone",
  "retreat_from_others",
  "avoid_contacts"
)
```

## Helper Functions

```{r helpers}
extract_condition_number <- function(condition_id) {
  if (is.na(condition_id) || !nzchar(as.character(condition_id))) {
    return(NA_real_)
  }

  raw <- sub(".*condition_([0-9]+).*", "\\1", as.character(condition_id), perl = TRUE)
  if (!grepl("^[0-9]+$", raw)) {
    return(NA_real_)
  }

  suppressWarnings(as.numeric(raw))
}

map_interaction_group <- function(condition_number) {
  key <- as.character(suppressWarnings(as.integer(condition_number)))
  if (is.na(condition_number) || !(key %in% names(INTERACTION_CONDITION_LABELS))) {
    return("Other")
  }
  INTERACTION_CONDITION_LABELS[[key]]
}

map_visualization_group <- function(condition_number, visualization_technique, condition_id, condition_name) {
  cn <- suppressWarnings(as.integer(condition_number))
  if (!is.na(cn) && cn == BASELINE_CONDITION_NUMBER) {
    return("Baseline")
  }

  technique_raw <- tolower(trimws(ifelse(is.na(visualization_technique), "", visualization_technique)))
  if (technique_raw == "baseline") {
    return("Baseline")
  }
  if (technique_raw == "confidence_interval") {
    return("PI")
  }
  if (technique_raw == "ensemble_plot") {
    return("Ensemble")
  }
  if (technique_raw == "combined_plot") {
    return("PI + Ensemble")
  }

  condition_id_raw <- tolower(trimws(ifelse(is.na(condition_id), "", condition_id)))
  if (grepl("_ci$", condition_id_raw)) {
    return("PI")
  }
  if (grepl("_ep$", condition_id_raw)) {
    return("Ensemble")
  }
  if (grepl("_ciep$", condition_id_raw)) {
    return("PI + Ensemble")
  }

  condition_name_raw <- tolower(trimws(ifelse(is.na(condition_name), "", condition_name)))
  if (grepl("baseline", condition_name_raw)) {
    return("Baseline")
  }
  if (grepl("combined", condition_name_raw)) {
    return("PI + Ensemble")
  }
  if (grepl("ensemble", condition_name_raw)) {
    return("Ensemble")
  }
  if (grepl("\\(ci\\)|confidence", condition_name_raw)) {
    return("PI")
  }

  "Other"
}

parse_response_json <- function(value) {
  if (is.na(value) || !nzchar(as.character(value))) {
    return(list())
  }

  parsed <- tryCatch(
    jsonlite::fromJSON(as.character(value), simplifyVector = TRUE),
    error = function(e) list()
  )

  if (is.null(parsed) || !is.list(parsed)) {
    return(list())
  }

  parsed
}

expand_response_columns <- function(data, response_col = "response") {
  if (!(response_col %in% names(data))) {
    return(data)
  }

  parsed <- lapply(data[[response_col]], parse_response_json)
  all_keys <- unique(unlist(lapply(parsed, names), use.names = FALSE))
  all_keys <- all_keys[!is.na(all_keys) & nzchar(all_keys)]

  out <- data

  for (key in all_keys) {
    extracted <- vapply(
      parsed,
      function(item) {
        value <- item[[key]]
        if (is.null(value) || length(value) == 0) {
          return(NA_character_)
        }
        as.character(value[[1]])
      },
      character(1)
    )

    if (key %in% names(out)) {
      existing <- out[[key]]
      fill_idx <- is.na(existing) | trimws(as.character(existing)) == ""
      existing[fill_idx] <- extracted[fill_idx]
      out[[key]] <- existing
    } else {
      out[[key]] <- extracted
    }
  }

  out
}

normalize_likert_0_6_to_1_7 <- function(values) {
  numeric_values <- suppressWarnings(as.numeric(values))
  valid <- numeric_values[!is.na(numeric_values)]

  if (length(valid) == 0) {
    return(numeric_values)
  }

  if (all(valid >= 0 & valid <= 6)) {
    return(pmin(pmax(numeric_values + 1, 1), 7))
  }

  numeric_values
}

set_sum_contrasts <- function(data, factors) {
  out <- data
  for (factor_name in factors) {
    out[[factor_name]] <- factor(out[[factor_name]])
    contrasts(out[[factor_name]]) <- contr.sum(length(levels(out[[factor_name]])))
  }
  out
}

identify_attention_check_failures <- function(data) {
  if (!all(c("trial_type", "participant_id") %in% names(data))) {
    return(character(0))
  }

  survey_rows <- data %>%
    dplyr::filter(trial_type == "trust-survey") %>%
    expand_response_columns("response")

  if (nrow(survey_rows) == 0) {
    return(character(0))
  }

  for (key in c(TRUST_ITEM_KEYS, INTERACTION_ITEM_KEYS)) {
    if (!(key %in% names(survey_rows))) {
      survey_rows[[key]] <- NA_real_
    }
    survey_rows[[key]] <- normalize_likert_0_6_to_1_7(survey_rows[[key]])
  }

  trust_complete <- rowSums(!is.na(survey_rows[, TRUST_ITEM_KEYS, drop = FALSE])) == length(TRUST_ITEM_KEYS)
  interaction_complete <- rowSums(!is.na(survey_rows[, INTERACTION_ITEM_KEYS, drop = FALSE])) == length(INTERACTION_ITEM_KEYS)

  trust_uniform <- apply(survey_rows[, TRUST_ITEM_KEYS, drop = FALSE], 1, function(x) {
    length(unique(stats::na.omit(x))) == 1
  })

  interaction_uniform <- apply(survey_rows[, INTERACTION_ITEM_KEYS, drop = FALSE], 1, function(x) {
    length(unique(stats::na.omit(x))) == 1
  })

  failed <- survey_rows$participant_id[trust_complete & interaction_complete & trust_uniform & interaction_uniform]
  unique(as.character(failed[!is.na(failed)]))
}

map_interaction_factor <- function(condition_number) {
  dplyr::case_when(
    condition_number %in% c(21, 22) ~ "hover",
    condition_number %in% c(23, 24) ~ "click",
    condition_number %in% c(25, 26) ~ "animation",
    TRUE ~ NA_character_
  )
}

map_detail_factor <- function(condition_number) {
  dplyr::case_when(
    condition_number %in% c(21, 23, 25) ~ "show_one",
    condition_number %in% c(22, 24, 26) ~ "show_all",
    TRUE ~ NA_character_
  )
}

map_vis_type <- function(visualization_group) {
  dplyr::case_when(
    visualization_group == "PI" ~ "CI",
    visualization_group == "Ensemble" ~ "EP",
    visualization_group == "PI + Ensemble" ~ "CIEP",
    TRUE ~ NA_character_
  )
}

read_participant_csv <- function(file_path) {
  df <- read.csv(file_path, stringsAsFactors = FALSE, check.names = FALSE)
  df$source_file <- basename(file_path)

  if (!("participant_id" %in% names(df)) || all(is.na(df$participant_id))) {
    token <- strsplit(tools::file_path_sans_ext(basename(file_path)), "_")[[1]]
    inferred_id <- ifelse(length(token) >= 2, token[[2]], NA_character_)
    df$participant_id <- inferred_id
  }

  if (!("condition_id" %in% names(df))) {
    df$condition_id <- NA_character_
  }
  if (!("condition_name" %in% names(df))) {
    df$condition_name <- NA_character_
  }

  df$condition_number <- vapply(df$condition_id, extract_condition_number, numeric(1))
  df$interaction_group <- vapply(df$condition_number, map_interaction_group, character(1))
  df$visualization_group <- mapply(
    map_visualization_group,
    condition_number = df$condition_number,
    visualization_technique = if ("visualization_technique" %in% names(df)) df$visualization_technique else NA_character_,
    condition_id = df$condition_id,
    condition_name = df$condition_name,
    USE.NAMES = FALSE
  )

  df
}
```

## Load and Filter Data

```{r load-data}
csv_files <- unlist(
  lapply(
    data_dirs,
    function(dir_path) {
      list.files(dir_path, pattern = params$csv_pattern, full.names = TRUE)
    }
  ),
  use.names = FALSE
)

if (length(csv_files) == 0) {
  stop(
    "No CSV files found in: ",
    paste(data_dirs, collapse = ", "),
    " with pattern ",
    params$csv_pattern
  )
}

combined_data <- dplyr::bind_rows(lapply(csv_files, read_participant_csv))

before_n <- dplyr::n_distinct(combined_data$participant_id)

combined_data <- combined_data %>%
  dplyr::filter(!is.na(participant_id)) %>%
  dplyr::filter(tolower(as.character(participant_id)) != "test")

attention_failures <- identify_attention_check_failures(combined_data)

if (length(attention_failures) > 0) {
  combined_data <- combined_data %>%
    dplyr::filter(!(as.character(participant_id) %in% attention_failures))
}

after_n <- dplyr::n_distinct(combined_data$participant_id)

cat("Data directories:\n")
cat(paste0("  - ", data_dirs), sep = "\n")
cat("\nCSV files loaded: ", length(csv_files), "\n", sep = "")
cat("Participants: ", before_n, " -> ", after_n, "\n", sep = "")
cat("Attention-check exclusions: ", length(attention_failures), "\n", sep = "")
```

## Personality-Survey Preprocessing (Participant Covariate)

```{r preprocess-personality-survey}
personality_rows_expanded <- combined_data %>%
  dplyr::filter(trial_type == "personality-survey") %>%
  expand_response_columns("response")

for (key in PERSONALITY_ITEM_KEYS) {
  if (!(key %in% names(personality_rows_expanded))) {
    personality_rows_expanded[[key]] <- NA_real_
  }
  personality_rows_expanded[[key]] <- suppressWarnings(as.numeric(personality_rows_expanded[[key]])) + 1
}

personality_participant <- personality_rows_expanded %>%
  dplyr::mutate(
    participant_id = as.character(participant_id),
    general_trust_composite = rowMeans(
      dplyr::select(., dplyr::all_of(PERSONALITY_ITEM_KEYS)),
      na.rm = TRUE
    )
  ) %>%
  dplyr::mutate(
    general_trust_composite = ifelse(
      is.finite(general_trust_composite),
      general_trust_composite,
      NA_real_
    )
  ) %>%
  dplyr::group_by(participant_id) %>%
  dplyr::summarise(
    general_trust_composite = mean(general_trust_composite, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    general_trust_composite = ifelse(
      is.finite(general_trust_composite),
      general_trust_composite,
      NA_real_
    )
  )

cat("Personality-survey rows (raw): ", nrow(personality_rows_expanded), "\n", sep = "")
cat("Participants with finite general_trust_composite: ", sum(is.finite(personality_participant$general_trust_composite)), "\n", sep = "")
```

## Trust-Survey Preprocessing

```{r preprocess-trust-survey}
trust_survey <- combined_data %>%
  dplyr::filter(trial_type == "trust-survey") %>%
  expand_response_columns("response")

for (key in c(TRUST_ITEM_KEYS, INTERACTION_ITEM_KEYS)) {
  if (!(key %in% names(trust_survey))) {
    trust_survey[[key]] <- NA_real_
  }
  trust_survey[[key]] <- normalize_likert_0_6_to_1_7(trust_survey[[key]])
}

trust_survey <- trust_survey %>%
  dplyr::mutate(
    skeptical_rating_rev = 8 - as.numeric(skeptical_rating),
    usability_difficulty_rev = 8 - as.numeric(usability_difficulty),
    composite_trust_score = rowMeans(
      cbind(
        skeptical_rating_rev,
        as.numeric(data_trust),
        usability_difficulty_rev,
        as.numeric(comprehension_ease)
      ),
      na.rm = TRUE
    ),
    interaction_experience = rowMeans(
      dplyr::across(dplyr::all_of(INTERACTION_ITEM_KEYS)),
      na.rm = TRUE
    ),
    interaction = map_interaction_factor(condition_number),
    detail_presentation = map_detail_factor(condition_number),
    vis_type = map_vis_type(visualization_group),
    interaction_group = vapply(condition_number, map_interaction_group, character(1))
  )

trust_survey$composite_trust_score[is.nan(trust_survey$composite_trust_score)] <- NA_real_
trust_survey$interaction_experience[is.nan(trust_survey$interaction_experience)] <- NA_real_

model_input_raw <- trust_survey %>%
  dplyr::filter(condition_number %in% TREATMENT_CONDITIONS) %>%
  dplyr::filter(
    !is.na(interaction),
    !is.na(detail_presentation),
    !is.na(vis_type),
    !is.na(composite_trust_score),
    !is.na(interaction_experience)
  )

# Aggregate if duplicate rows exist for a participant x condition cell.
model_input <- model_input_raw %>%
  dplyr::group_by(participant_id, vis_type, interaction, detail_presentation) %>%
  dplyr::summarise(
    composite_trust_score = mean(composite_trust_score, na.rm = TRUE),
    interaction_experience = mean(interaction_experience, na.rm = TRUE),
    .groups = "drop"
  )

# Complete within-subject grid for interaction (3) x detail_presentation (2) = 6 cells.
participant_cell_counts <- model_input %>%
  dplyr::count(participant_id, name = "n_cells")

complete_participants <- participant_cell_counts %>%
  dplyr::filter(n_cells == 6) %>%
  dplyr::pull(participant_id)

model_data <- model_input %>%
  dplyr::filter(participant_id %in% complete_participants) %>%
  dplyr::mutate(
    participant_id = factor(participant_id),
    interaction = factor(interaction, levels = c("hover", "click", "animation")),
    detail_presentation = factor(detail_presentation, levels = c("show_one", "show_all")),
    vis_type = factor(vis_type, levels = c("CI", "EP", "CIEP"))
  )

cat("Trust-survey rows (raw): ", nrow(trust_survey), "\n", sep = "")
cat("Model rows after filtering: ", nrow(model_data), "\n", sep = "")
cat("Model participants (complete 6-cell within-subject grid): ", dplyr::n_distinct(model_data$participant_id), "\n", sep = "")
```

## Section 7: Cross-Interaction Technique Summary

```{r section-7-summary}
section7_summary <- model_data %>%
  dplyr::group_by(interaction, detail_presentation) %>%
  dplyr::summarise(
    n = dplyr::n(),
    trust_mean = mean(composite_trust_score, na.rm = TRUE),
    trust_sd = stats::sd(composite_trust_score, na.rm = TRUE),
    trust_se = trust_sd / sqrt(n),
    interaction_mean = mean(interaction_experience, na.rm = TRUE),
    interaction_sd = stats::sd(interaction_experience, na.rm = TRUE),
    interaction_se = interaction_sd / sqrt(n),
    .groups = "drop"
  ) %>%
  dplyr::arrange(interaction, detail_presentation)

knitr::kable(section7_summary, digits = 3, caption = "Section 7 summary by interaction x detail presentation")
```

## Section 8: Interaction x Visualization Grid Summary

```{r section-8-summary}
section8_summary <- model_data %>%
  dplyr::group_by(vis_type, interaction, detail_presentation) %>%
  dplyr::summarise(
    n = dplyr::n(),
    trust_mean = mean(composite_trust_score, na.rm = TRUE),
    trust_sd = stats::sd(composite_trust_score, na.rm = TRUE),
    trust_se = trust_sd / sqrt(n),
    interaction_mean = mean(interaction_experience, na.rm = TRUE),
    interaction_sd = stats::sd(interaction_experience, na.rm = TRUE),
    interaction_se = interaction_sd / sqrt(n),
    .groups = "drop"
  ) %>%
  dplyr::arrange(vis_type, interaction, detail_presentation)

knitr::kable(section8_summary, digits = 3, caption = "Section 8 summary by vis_type x interaction condition")
```

## Regression 1: Trust

```{r regression-trust}
regression_model_data <- set_sum_contrasts(
  model_data,
  factors = c("vis_type", "interaction", "detail_presentation")
)

trust_rows_before_covariate <- nrow(regression_model_data)
trust_participants_before_covariate <- dplyr::n_distinct(regression_model_data$participant_id)

trust_model_data <- regression_model_data %>%
  dplyr::mutate(participant_id = as.character(participant_id)) %>%
  dplyr::left_join(personality_participant, by = "participant_id") %>%
  dplyr::filter(is.finite(general_trust_composite)) %>%
  dplyr::mutate(participant_id = factor(participant_id))

trust_rows_after_covariate <- nrow(trust_model_data)
trust_participants_after_covariate <- dplyr::n_distinct(trust_model_data$participant_id)
trust_rows_lost_covariate <- trust_rows_before_covariate - trust_rows_after_covariate

cat("Trust model rows before covariate join: ", trust_rows_before_covariate, "\n", sep = "")
cat("Trust model rows after covariate join: ", trust_rows_after_covariate, "\n", sep = "")
cat("Trust model row loss from covariate filter: ", trust_rows_lost_covariate, "\n", sep = "")
cat("Trust model participants before/after covariate join: ", trust_participants_before_covariate, " -> ", trust_participants_after_covariate, "\n", sep = "")

trust_lm <- lm(
  composite_trust_score ~ vis_type * interaction * detail_presentation + general_trust_composite + participant_id,
  data = trust_model_data,
  na.action = na.exclude
)

trust_anova <- anova(trust_lm)
trust_anova
```

## Regression 1: Trust (Joint Effects)

```{r regression-trust-joint-effects}
trust_joint_lm <- trust_lm
trust_joint_anova <- trust_anova
trust_joint_anova
```

## Regression 2: Interaction Experience

```{r regression-interaction-experience}
interaction_lm <- lm(
  interaction_experience ~ vis_type * interaction * detail_presentation + participant_id,
  data = regression_model_data,
  na.action = na.exclude
)

interaction_anova <- anova(interaction_lm)
interaction_anova
```

## Regression 2: Interaction Experience (Joint Effects)

```{r regression-interaction-experience-joint-effects}
interaction_joint_lm <- interaction_lm
interaction_joint_anova <- interaction_anova
interaction_joint_anova
```

## EMMs: Interaction

```{r emmeans-interaction}
extract_emmean_with_sd <- function(model, factor_name, sd_data, value_col) {
  emmean_tbl <- emmeans::emmeans(
    model,
    specs = stats::as.formula(paste0("~ ", factor_name))
  ) %>%
    as.data.frame() %>%
    dplyr::select(dplyr::all_of(factor_name), emmean, SE)

  sd_tbl <- sd_data %>%
    dplyr::group_by(.data[[factor_name]]) %>%
    dplyr::summarise(
      sd = stats::sd(.data[[value_col]], na.rm = TRUE),
      .groups = "drop"
    )

  emmean_tbl %>%
    dplyr::left_join(sd_tbl, by = factor_name)
}

extract_tukey_pairwise <- function(model, factor_name) {
  emmean_obj <- emmeans::emmeans(
    model,
    specs = stats::as.formula(paste0("~ ", factor_name))
  )

  as.data.frame(
    summary(
      emmeans::contrast(emmean_obj, method = "pairwise", adjust = "tukey"),
      infer = c(TRUE, TRUE)
    )
  )
}

label_q123_condition <- function(interaction_mode, detail_presentation) {
  interaction_label <- dplyr::case_when(
    interaction_mode == "hover" ~ "Hover",
    interaction_mode == "click" ~ "Click",
    TRUE ~ as.character(interaction_mode)
  )

  detail_label <- dplyr::case_when(
    detail_presentation == "show_one" ~ "Show One",
    detail_presentation == "show_all" ~ "Show All",
    TRUE ~ as.character(detail_presentation)
  )

  paste(interaction_label, detail_label)
}

interaction_level_scores <- model_data %>%
  dplyr::group_by(participant_id, interaction) %>%
  dplyr::summarise(
    composite_trust_score = mean(composite_trust_score, na.rm = TRUE),
    interaction_experience = mean(interaction_experience, na.rm = TRUE),
    .groups = "drop"
  )

trust_interaction_emmeans <- extract_emmean_with_sd(
  model = trust_joint_lm,
  factor_name = "interaction",
  sd_data = interaction_level_scores,
  value_col = "composite_trust_score"
)

interactionexp_interaction_emmeans <- extract_emmean_with_sd(
  model = interaction_joint_lm,
  factor_name = "interaction",
  sd_data = interaction_level_scores,
  value_col = "interaction_experience"
)

trust_interaction_tukey <- extract_tukey_pairwise(
  model = trust_joint_lm,
  factor_name = "interaction"
)

interactionexp_interaction_tukey <- extract_tukey_pairwise(
  model = interaction_joint_lm,
  factor_name = "interaction"
)

knitr::kable(trust_interaction_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for interaction (trust)")
knitr::kable(interactionexp_interaction_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for interaction (interaction experience)")
knitr::kable(trust_interaction_tukey, digits = 4, caption = "Tukey pairwise comparisons for interaction (trust)")
knitr::kable(interactionexp_interaction_tukey, digits = 4, caption = "Tukey pairwise comparisons for interaction (interaction experience)")
```

## EMMs: Visualization Type

```{r emmeans-vis-type}
# vis_type is between-subject here (one vis_type per participant), so it is
# non-estimable in models that include participant_id fixed effects.
# Use equivalent vis_type models without participant_id fixed effects.
trust_vistype_lm <- lm(
  composite_trust_score ~ vis_type * interaction * detail_presentation + general_trust_composite,
  data = trust_model_data,
  na.action = na.exclude
)

interactionexp_vistype_lm <- lm(
  interaction_experience ~ vis_type * interaction * detail_presentation,
  data = regression_model_data,
  na.action = na.exclude
)

cat(
  "Note: vis_type is nested within participant_id in the joint fixed-effect models; ",
  "vis_type EMMs and Tukey comparisons below are estimated from models without participant_id fixed effects.\n",
  sep = ""
)

trust_vistype_level_scores <- trust_model_data %>%
  dplyr::group_by(participant_id, vis_type) %>%
  dplyr::summarise(
    composite_trust_score = mean(composite_trust_score, na.rm = TRUE),
    .groups = "drop"
  )

interactionexp_vistype_level_scores <- regression_model_data %>%
  dplyr::group_by(participant_id, vis_type) %>%
  dplyr::summarise(
    interaction_experience = mean(interaction_experience, na.rm = TRUE),
    .groups = "drop"
  )

trust_vistype_emmeans <- extract_emmean_with_sd(
  model = trust_vistype_lm,
  factor_name = "vis_type",
  sd_data = trust_vistype_level_scores,
  value_col = "composite_trust_score"
)

interactionexp_vistype_emmeans <- extract_emmean_with_sd(
  model = interactionexp_vistype_lm,
  factor_name = "vis_type",
  sd_data = interactionexp_vistype_level_scores,
  value_col = "interaction_experience"
)

trust_vistype_tukey <- extract_tukey_pairwise(
  model = trust_vistype_lm,
  factor_name = "vis_type"
)

interactionexp_vistype_tukey <- extract_tukey_pairwise(
  model = interactionexp_vistype_lm,
  factor_name = "vis_type"
)

knitr::kable(trust_vistype_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for vis_type (trust)")
knitr::kable(interactionexp_vistype_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for vis_type (interaction experience)")
knitr::kable(trust_vistype_tukey, digits = 4, caption = "Tukey pairwise comparisons for vis_type (trust)")
knitr::kable(interactionexp_vistype_tukey, digits = 4, caption = "Tukey pairwise comparisons for vis_type (interaction experience)")
```

## EMMs: Detail Presentation

```{r emmeans-detail-presentation}
detail_level_scores <- model_data %>%
  dplyr::group_by(participant_id, detail_presentation) %>%
  dplyr::summarise(
    composite_trust_score = mean(composite_trust_score, na.rm = TRUE),
    interaction_experience = mean(interaction_experience, na.rm = TRUE),
    .groups = "drop"
  )

trust_detail_emmeans <- extract_emmean_with_sd(
  model = trust_joint_lm,
  factor_name = "detail_presentation",
  sd_data = detail_level_scores,
  value_col = "composite_trust_score"
)

interactionexp_detail_emmeans <- extract_emmean_with_sd(
  model = interaction_joint_lm,
  factor_name = "detail_presentation",
  sd_data = detail_level_scores,
  value_col = "interaction_experience"
)

trust_detail_tukey <- extract_tukey_pairwise(
  model = trust_joint_lm,
  factor_name = "detail_presentation"
)

interactionexp_detail_tukey <- extract_tukey_pairwise(
  model = interaction_joint_lm,
  factor_name = "detail_presentation"
)

knitr::kable(trust_detail_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for detail_presentation (trust)")
knitr::kable(interactionexp_detail_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for detail_presentation (interaction experience)")
knitr::kable(trust_detail_tukey, digits = 4, caption = "Tukey pairwise comparisons for detail_presentation (trust)")
knitr::kable(interactionexp_detail_tukey, digits = 4, caption = "Tukey pairwise comparisons for detail_presentation (interaction experience)")
```

## Additional Analysis: Q1-Q3 (Click/Hover x Detail Presentation x Visualization Type; No Baseline)

```{r q1-q3-data-prep}
prediction_q123_raw <- combined_data %>%
  dplyr::filter(trial_type == "prediction-task") %>%
  dplyr::mutate(
    probability = suppressWarnings(as.numeric(probability_estimate)),
    city_a_estimate = suppressWarnings(as.numeric(city_a_estimate)),
    city_b_estimate = suppressWarnings(as.numeric(city_b_estimate)),
    estimated_value_row = rowMeans(cbind(city_a_estimate, city_b_estimate), na.rm = TRUE),
    estimated_value_row = ifelse(is.finite(estimated_value_row), estimated_value_row, NA_real_),
    interaction_mode = map_interaction_factor(condition_number),
    detail_presentation = map_detail_factor(condition_number),
    vistype = map_vis_type(visualization_group),
    decision_result_row = dplyr::case_when(
      !is.na(travel_choice) & !is.na(city_a_label) & travel_choice == city_a_label ~ "A",
      !is.na(travel_choice) & !is.na(city_b_label) & travel_choice == city_b_label ~ "B",
      tolower(trimws(as.character(travel_choice))) == "no preference" ~ "No Preference",
      TRUE ~ NA_character_
    )
  ) %>%
  dplyr::filter(condition_number %in% TREATMENT_CONDITIONS) %>%
  dplyr::filter(interaction_mode %in% c("hover", "click")) %>%
  dplyr::filter(!is.na(vistype), !is.na(detail_presentation), !is.na(interaction_mode))

mode_or_na <- function(x) {
  x <- as.character(x)
  x <- x[!is.na(x) & nzchar(x)]
  if (length(x) == 0) {
    return(NA_character_)
  }
  names(sort(table(x), decreasing = TRUE))[1]
}

prediction_q123_condition <- prediction_q123_raw %>%
  dplyr::group_by(participant_id, condition_number, condition_name, vistype, interaction_mode, detail_presentation) %>%
  dplyr::summarise(
    probability = mean(probability, na.rm = TRUE),
    estimated_value = mean(estimated_value_row, na.rm = TRUE),
    decision_result = mode_or_na(decision_result_row),
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    probability = ifelse(is.finite(probability), probability, NA_real_),
    estimated_value = ifelse(is.finite(estimated_value), estimated_value, NA_real_),
    participant_id = factor(participant_id),
    vistype = factor(vistype, levels = c("CI", "EP", "CIEP")),
    interaction_mode = factor(interaction_mode, levels = c("hover", "click")),
    detail_presentation = factor(detail_presentation, levels = c("show_one", "show_all")),
    decision_result = factor(decision_result, levels = c("A", "B", "No Preference"))
  ) %>%
  droplevels()

# Require complete within-subject grid for click/hover x detail (2 x 2 = 4 cells).
q123_participant_cell_counts <- prediction_q123_condition %>%
  dplyr::count(participant_id, name = "n_cells")

q123_complete_participants <- q123_participant_cell_counts %>%
  dplyr::filter(n_cells == 4) %>%
  dplyr::pull(participant_id)

prediction_q123_model_base <- prediction_q123_condition %>%
  dplyr::filter(participant_id %in% q123_complete_participants) %>%
  droplevels()

q123_q1_data <- prediction_q123_model_base %>%
  dplyr::filter(is.finite(probability))

q123_q2_data <- prediction_q123_model_base %>%
  dplyr::filter(is.finite(estimated_value))

q123_q3_data <- prediction_q123_model_base %>%
  dplyr::filter(!is.na(decision_result)) %>%
  droplevels()

cat("Q1/Q2/Q3 rows after filtering: ", nrow(prediction_q123_model_base), "\n", sep = "")
cat("Q1/Q2/Q3 participants (complete 4-cell grid): ", dplyr::n_distinct(prediction_q123_model_base$participant_id), "\n", sep = "")
```

### Q1: Probability (Continuous)

```{r q1-models}
q123_q1_model_data <- set_sum_contrasts(
  q123_q1_data,
  factors = c("vistype", "interaction_mode", "detail_presentation")
)

# Repeated-measures best-practice model
q123_q1_lmer <- lmer(
  probability ~ vistype * interaction_mode * detail_presentation + (1 | participant_id),
  data = q123_q1_model_data,
  REML = FALSE,
  na.action = na.exclude
)

anova(q123_q1_lmer, type = 3)

q123_q1_treatment_emm_obj <- emmeans(
  q123_q1_lmer,
  ~ interaction_mode * detail_presentation,
  weights = "proportional"
)

q123_q1_treatment_emm <- as.data.frame(
  summary(
    q123_q1_treatment_emm_obj,
    infer = c(TRUE, FALSE)
  )
) %>%
  dplyr::mutate(
    condition_label = label_q123_condition(interaction_mode, detail_presentation),
    condition_label = factor(
      condition_label,
      levels = c("Hover Show One", "Hover Show All", "Click Show One", "Click Show All")
    )
  ) %>%
  dplyr::arrange(condition_label)

q123_q1_condition_emmeans <- q123_q1_treatment_emm %>%
  dplyr::select(condition_label, interaction_mode, detail_presentation, emmean, SE, df, lower.CL, upper.CL)

q123_q1_tukey_pairwise <- as.data.frame(
  summary(
    emmeans::contrast(q123_q1_treatment_emm_obj, method = "pairwise", adjust = "tukey"),
    infer = c(TRUE, TRUE)
  )
)

knitr::kable(
  q123_q1_condition_emmeans,
  digits = 3,
  caption = "Q1 EMMs for Treatment Conditions (No Baseline)"
)
knitr::kable(
  q123_q1_tukey_pairwise,
  digits = 3,
  caption = "Q1 Tukey pairwise comparisons for treatment conditions (No Baseline)"
)
```

### Q2: Estimated Prediction Value (Continuous)

```{r q2-models}
q123_q2_model_data <- set_sum_contrasts(
  q123_q2_data,
  factors = c("vistype", "interaction_mode", "detail_presentation")
)

# Repeated-measures best-practice model
q123_q2_lmer <- lmer(
  estimated_value ~ vistype * interaction_mode * detail_presentation + (1 | participant_id),
  data = q123_q2_model_data,
  REML = FALSE,
  na.action = na.exclude
)

anova(q123_q2_lmer, type = 3)

q123_q2_treatment_emm_obj <- emmeans(
  q123_q2_lmer,
  ~ interaction_mode * detail_presentation,
  weights = "proportional"
)

q123_q2_treatment_emm <- as.data.frame(
  summary(
    q123_q2_treatment_emm_obj,
    infer = c(TRUE, FALSE)
  )
) %>%
  dplyr::mutate(
    condition_label = label_q123_condition(interaction_mode, detail_presentation),
    condition_label = factor(
      condition_label,
      levels = c("Hover Show One", "Hover Show All", "Click Show One", "Click Show All")
    )
  ) %>%
  dplyr::arrange(condition_label)

q123_q2_condition_emmeans <- q123_q2_treatment_emm %>%
  dplyr::select(condition_label, interaction_mode, detail_presentation, emmean, SE, df, lower.CL, upper.CL)

q123_q2_tukey_pairwise <- as.data.frame(
  summary(
    emmeans::contrast(q123_q2_treatment_emm_obj, method = "pairwise", adjust = "tukey"),
    infer = c(TRUE, TRUE)
  )
)

knitr::kable(
  q123_q2_condition_emmeans,
  digits = 3,
  caption = "Q2 EMMs for Treatment Conditions (No Baseline)"
)
knitr::kable(
  q123_q2_tukey_pairwise,
  digits = 3,
  caption = "Q2 Tukey pairwise comparisons for treatment conditions (No Baseline)"
)
```

### Q3: Decision Result (A, B, No Preference; Nominal)

```{r q3-models}
q123_q3_model_data <- q123_q3_data %>%
  dplyr::mutate(
    decision_result = factor(decision_result, levels = c("A", "B", "No Preference")),
    interaction_mode = factor(as.character(interaction_mode), levels = c("hover", "click")),
    detail_presentation = factor(as.character(detail_presentation), levels = c("show_one", "show_all")),
    vistype = factor(
      dplyr::recode(
        as.character(vistype),
        "CI" = "PI",
        "EP" = "Ensemble",
        "CIEP" = "PI + Ensemble"
      ),
      levels = c("PI + Ensemble", "PI", "Ensemble")
    )
  ) %>%
  droplevels()

condition_levels <- paste0(
  "Condition ",
  sort(unique(q123_q3_model_data$condition_number))
)

q123_q3_model_data <- q123_q3_model_data %>%
  dplyr::mutate(
    condition_label = paste0("Condition ", condition_number),
    condition_label = factor(condition_label, levels = condition_levels)
  )

q3_condition_portion <- q123_q3_model_data %>%
  dplyr::count(condition_label, decision_result, .drop = FALSE, name = "n") %>%
  dplyr::group_by(condition_label) %>%
  dplyr::mutate(
    total = sum(n),
    portion = ifelse(total > 0, n / total, 0)
  ) %>%
  dplyr::ungroup()

ggplot(q3_condition_portion, aes(x = condition_label, y = portion, fill = decision_result)) +
  geom_col(position = "stack", width = 0.7) +
  scale_y_continuous(
    limits = c(0, 1),
    labels = function(x) paste0(round(x * 100), "%")
  ) +
  labs(
    title = "Q3 Decision Portion by Condition",
    x = "Condition",
    y = "Decision Portion",
    fill = "Decision"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

q3_condition_portion_table <- q3_condition_portion %>%
  dplyr::group_by(condition_label) %>%
  dplyr::summarise(
    A = portion[decision_result == "A"][1],
    B = portion[decision_result == "B"][1],
    `No preference` = portion[decision_result == "No Preference"][1],
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    dplyr::across(c(A, B, `No preference`), ~ round(ifelse(is.na(.x), 0, .x), 4))
  )

knitr::kable(
  q3_condition_portion_table,
  caption = "Q3 Decision Portion Table by Condition"
)

q3_treatment_data <- q123_q3_model_data %>%
  droplevels()

q3_interaction_mode_portion <- q3_treatment_data %>%
  dplyr::count(interaction_mode, decision_result, .drop = FALSE, name = "n") %>%
  dplyr::group_by(interaction_mode) %>%
  dplyr::mutate(
    total = sum(n),
    portion = ifelse(total > 0, n / total, 0)
  ) %>%
  dplyr::ungroup()

ggplot(q3_interaction_mode_portion, aes(x = interaction_mode, y = portion, fill = decision_result)) +
  geom_col(position = "stack", width = 0.7) +
  scale_y_continuous(
    limits = c(0, 1),
    labels = function(x) paste0(round(x * 100), "%")
  ) +
  labs(
    title = "Q3 Decision Portion by Interaction Type (Treatment Only)",
    x = "Interaction Type",
    y = "Decision Portion",
    fill = "Decision"
  ) +
  theme_minimal()

q3_interaction_mode_portion_table <- q3_interaction_mode_portion %>%
  dplyr::group_by(interaction_mode) %>%
  dplyr::summarise(
    A = portion[decision_result == "A"][1],
    B = portion[decision_result == "B"][1],
    `No preference` = portion[decision_result == "No Preference"][1],
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    dplyr::across(c(A, B, `No preference`), ~ round(ifelse(is.na(.x), 0, .x), 4))
  )

knitr::kable(
  q3_interaction_mode_portion_table,
  caption = "Q3 Decision Portion Table by Interaction Type (hover vs click; treatment only)"
)

q3_detail_portion <- q3_treatment_data %>%
  dplyr::count(detail_presentation, decision_result, .drop = FALSE, name = "n") %>%
  dplyr::group_by(detail_presentation) %>%
  dplyr::mutate(
    total = sum(n),
    portion = ifelse(total > 0, n / total, 0)
  ) %>%
  dplyr::ungroup()

ggplot(q3_detail_portion, aes(x = detail_presentation, y = portion, fill = decision_result)) +
  geom_col(position = "stack", width = 0.7) +
  scale_y_continuous(
    limits = c(0, 1),
    labels = function(x) paste0(round(x * 100), "%")
  ) +
  labs(
    title = "Q3 Decision Portion by Detail Presentation Type (Treatment Only)",
    x = "Detail Presentation Type",
    y = "Decision Portion",
    fill = "Decision"
  ) +
  theme_minimal()

q3_detail_portion_table <- q3_detail_portion %>%
  dplyr::group_by(detail_presentation) %>%
  dplyr::summarise(
    A = portion[decision_result == "A"][1],
    B = portion[decision_result == "B"][1],
    `No preference` = portion[decision_result == "No Preference"][1],
    .groups = "drop"
  ) %>%
  dplyr::mutate(
    dplyr::across(c(A, B, `No preference`), ~ round(ifelse(is.na(.x), 0, .x), 4))
  )

knitr::kable(
  q3_detail_portion_table,
  caption = "Q3 Decision Portion Table by Detail Presentation Type (show_one vs show_all; treatment only)"
)

q3_interaction_mode_frequency <- q3_treatment_data %>%
  dplyr::filter(!is.na(interaction_mode), !is.na(decision_result)) %>%
  dplyr::count(interaction_mode, decision_result, .drop = FALSE, name = "n")

q3_interaction_mode_frequency_xtab <- xtabs(
  n ~ interaction_mode + decision_result,
  data = q3_interaction_mode_frequency
)

knitr::kable(
  as.data.frame.matrix(q3_interaction_mode_frequency_xtab),
  caption = "Q3 Frequency Table (A/B/No Preference) by Interaction Type (hover vs click; treatment only)"
)

q3_interaction_mode_chisq <- NULL
if (
  nrow(q3_interaction_mode_frequency_xtab) > 1 &&
  ncol(q3_interaction_mode_frequency_xtab) > 1 &&
  all(rowSums(q3_interaction_mode_frequency_xtab) > 0) &&
  all(colSums(q3_interaction_mode_frequency_xtab) > 0)
) {
  q3_interaction_mode_chisq <- suppressWarnings(chisq.test(q3_interaction_mode_frequency_xtab))
}

q3_interaction_mode_chisq_summary <- if (!is.null(q3_interaction_mode_chisq)) {
  data.frame(
    predictor = "Interaction type (hover vs click)",
    chi_square = unname(q3_interaction_mode_chisq$statistic),
    df = unname(q3_interaction_mode_chisq$parameter),
    p_value = unname(q3_interaction_mode_chisq$p.value),
    note = ""
  )
} else {
  data.frame(
    predictor = "Interaction type (hover vs click)",
    chi_square = NA_real_,
    df = NA_real_,
    p_value = NA_real_,
    note = "Chi-square test skipped: not enough non-zero cells."
  )
}

q3_interaction_mode_chisq_summary <- q3_interaction_mode_chisq_summary %>%
  dplyr::mutate(
    chi_square = round(chi_square, 4),
    p_value = signif(p_value, 4)
  )

knitr::kable(
  q3_interaction_mode_chisq_summary,
  caption = "Q3 Chi-square Test by Interaction Type (hover vs click; treatment only)"
)

q3_detail_frequency <- q3_treatment_data %>%
  dplyr::filter(!is.na(detail_presentation), !is.na(decision_result)) %>%
  dplyr::count(detail_presentation, decision_result, .drop = FALSE, name = "n")

q3_detail_frequency_xtab <- xtabs(
  n ~ detail_presentation + decision_result,
  data = q3_detail_frequency
)

knitr::kable(
  as.data.frame.matrix(q3_detail_frequency_xtab),
  caption = "Q3 Frequency Table (A/B/No Preference) by Detail Presentation Type (show_one vs show_all; treatment only)"
)

q3_detail_chisq <- NULL
if (
  nrow(q3_detail_frequency_xtab) > 1 &&
  ncol(q3_detail_frequency_xtab) > 1 &&
  all(rowSums(q3_detail_frequency_xtab) > 0) &&
  all(colSums(q3_detail_frequency_xtab) > 0)
) {
  q3_detail_chisq <- suppressWarnings(chisq.test(q3_detail_frequency_xtab))
}

q3_detail_chisq_summary <- if (!is.null(q3_detail_chisq)) {
  data.frame(
    predictor = "Detail presentation type (show_one vs show_all)",
    chi_square = unname(q3_detail_chisq$statistic),
    df = unname(q3_detail_chisq$parameter),
    p_value = unname(q3_detail_chisq$p.value),
    note = ""
  )
} else {
  data.frame(
    predictor = "Detail presentation type (show_one vs show_all)",
    chi_square = NA_real_,
    df = NA_real_,
    p_value = NA_real_,
    note = "Chi-square test skipped: not enough non-zero cells."
  )
}

q3_detail_chisq_summary <- q3_detail_chisq_summary %>%
  dplyr::mutate(
    chi_square = round(chi_square, 4),
    p_value = signif(p_value, 4)
  )

knitr::kable(
  q3_detail_chisq_summary,
  caption = "Q3 Chi-square Test by Detail Presentation Type (show_one vs show_all; treatment only)"
)

# Pairwise comparisons for selecting A by visualization type.
q3_vistype_a_frequency <- q3_treatment_data %>%
  dplyr::mutate(
    vistype_label = factor(
      dplyr::recode(
        as.character(vistype),
        "PI" = "CI",
        "Ensemble" = "EP",
        "PI + Ensemble" = "CIEP"
      ),
      levels = c("CI", "EP", "CIEP")
    ),
    selected_A = factor(
      ifelse(decision_result == "A", "A", "Not A"),
      levels = c("A", "Not A")
    )
  ) %>%
  dplyr::count(vistype_label, selected_A, .drop = FALSE, name = "n")

q3_vistype_a_frequency_xtab <- xtabs(
  n ~ vistype_label + selected_A,
  data = q3_vistype_a_frequency
)

knitr::kable(
  as.data.frame.matrix(q3_vistype_a_frequency_xtab),
  caption = "Q3 Frequency Table for Selecting A by Visualization Type"
)

q3_vistype_a_pair_definitions <- data.frame(
  first_vistype = c("CI", "CI", "EP"),
  second_vistype = c("CIEP", "EP", "CIEP"),
  stringsAsFactors = FALSE
)

q3_vistype_a_pairwise <- dplyr::bind_rows(lapply(
  seq_len(nrow(q3_vistype_a_pair_definitions)),
  function(i) {
    first_vistype <- q3_vistype_a_pair_definitions$first_vistype[i]
    second_vistype <- q3_vistype_a_pair_definitions$second_vistype[i]

    comparison_xtab <- q3_vistype_a_frequency_xtab[
      c(first_vistype, second_vistype),
      c("A", "Not A"),
      drop = FALSE
    ]

    fisher_result <- fisher.test(comparison_xtab)

    first_A <- unname(comparison_xtab[first_vistype, "A"])
    first_not_A <- unname(comparison_xtab[first_vistype, "Not A"])
    second_A <- unname(comparison_xtab[second_vistype, "A"])
    second_not_A <- unname(comparison_xtab[second_vistype, "Not A"])

    first_total <- first_A + first_not_A
    second_total <- second_A + second_not_A

    first_prop_A <- ifelse(first_total > 0, first_A / first_total, NA_real_)
    second_prop_A <- ifelse(second_total > 0, second_A / second_total, NA_real_)
    times_more_likely_A <- ifelse(
      is.na(second_prop_A) || second_prop_A == 0,
      NA_real_,
      first_prop_A / second_prop_A
    )

    data.frame(
      comparison = paste(first_vistype, "vs", second_vistype),
      first_vistype = first_vistype,
      first_A = first_A,
      first_not_A = first_not_A,
      first_prop_A = first_prop_A,
      second_vistype = second_vistype,
      second_A = second_A,
      second_not_A = second_not_A,
      second_prop_A = second_prop_A,
      times_more_likely_A = times_more_likely_A,
      fisher_odds_ratio = unname(fisher_result$estimate),
      fisher_conf_low = unname(fisher_result$conf.int[1]),
      fisher_conf_high = unname(fisher_result$conf.int[2]),
      fisher_p_value = unname(fisher_result$p.value),
      stringsAsFactors = FALSE
    )
  }
))

q3_vistype_a_pairwise <- q3_vistype_a_pairwise %>%
  dplyr::mutate(
    dplyr::across(
      c(
        first_prop_A,
        second_prop_A,
        times_more_likely_A,
        fisher_odds_ratio,
        fisher_conf_low,
        fisher_conf_high
      ),
      ~ round(.x, 4)
    ),
    fisher_p_value = signif(fisher_p_value, 4)
  )

knitr::kable(
  q3_vistype_a_pairwise,
  caption = "Q3 Selecting A: Pairwise Times-More-Likely Comparisons and Fisher's Exact Tests"
)
```
