---
title: "Experiment 3 Section 7/8 Replication: Trust and Interaction Experience Regression"
output:
  html_document: default
  pdf_document: default
params:
  data_dirs:
    - "../data/0318/data"
    - "../data/0319/data"
    - "../data/0322/data"
  csv_pattern: "^user_.*\\.csv$"
  alpha: 0.05
  seed: 20260323
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(params$seed)
```

```{r table-spacing-style, results='asis', echo=FALSE}
table_column_padding_html <- "2rem"
table_column_padding_latex <- "10pt"

if (knitr::is_html_output()) {
  cat(
    "<style>\n",
    "table th,\n",
    "table td {\n",
    "  padding-left: ", table_column_padding_html, " !important;\n",
    "  padding-right: ", table_column_padding_html, " !important;\n",
    "}\n",
    "</style>\n",
    sep = ""
  )
}

if (knitr::is_latex_output()) {
  cat("\\setlength{\\tabcolsep}{", table_column_padding_latex, "}\n", sep = "")
}
```

## Goal

Replicate Experiment 3 notebook Section 7 and Section 8 analysis structure with two regression outcomes:

- `composite_trust_score ~ vis_type * interaction * detail_presentation`
- `interaction_experience ~ vis_type * interaction * detail_presentation`

This report follows the same trust-survey preprocessing used in `analysis-0318.ipynb`, including:

- loading `0318`, `0319`, `0322` batches
- extracting trust/interaction items from `response`
- normalizing Likert items from `0-6` to `1-7` when needed
- excluding attention-check failures

## Packages

```{r packages}
required_packages <- c(
  "dplyr",
  "jsonlite",
  "knitr",
  "emmeans"
)

missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)
]

if (length(missing_packages) > 0) {
  stop(
    "Missing required packages: ",
    paste(missing_packages, collapse = ", "),
    ". Install them before rendering."
  )
}

lapply(required_packages, library, character.only = TRUE)
```

## Paths

```{r paths}
report_dir <- local({
  current_input <- tryCatch(
    knitr::current_input(),
    error = function(e) character(0)
  )

  if (length(current_input) == 1 && nzchar(current_input)) {
    input_path <- current_input

    if (!grepl("^(/|[A-Za-z]:[/\\\\])", input_path)) {
      input_path <- file.path(getwd(), input_path)
    }

    if (grepl("\\.[Rr]md$", input_path) || file.exists(input_path)) {
      return(normalizePath(dirname(input_path), winslash = "/", mustWork = TRUE))
    }
  }

  fallback_dir <- file.path(getwd(), "Experiment3", "analysis")
  normalizePath(fallback_dir, winslash = "/", mustWork = TRUE)
})

resolve_report_path <- function(path_value) {
  if (grepl("^(/|[A-Za-z]:[/\\\\])", path_value)) {
    return(normalizePath(path_value, winslash = "/", mustWork = TRUE))
  }

  normalizePath(
    file.path(report_dir, path_value),
    winslash = "/",
    mustWork = TRUE
  )
}

data_dirs <- vapply(params$data_dirs, resolve_report_path, character(1))
```

## Constants

```{r constants}
BASELINE_CONDITION_NUMBER <- 1
TREATMENT_CONDITIONS <- c(21, 22, 23, 24, 25, 26)

INTERACTION_CONDITION_LABELS <- c(
  "1" = "Baseline",
  "21" = "Hover Show One",
  "22" = "Hover Show All",
  "23" = "Click Show One",
  "24" = "Click Show All",
  "25" = "Animation Show One",
  "26" = "Animation Show All"
)

SECTION7_INTERACTION_ORDER <- c(
  "Hover Show One",
  "Hover Show All",
  "Click Show One",
  "Click Show All",
  "Animation Show One",
  "Animation Show All"
)

TRUST_ITEM_KEYS <- c(
  "skeptical_rating",
  "data_trust",
  "usability_difficulty",
  "comprehension_ease"
)

INTERACTION_ITEM_KEYS <- c(
  "navigation_control",
  "content_control",
  "pace_control",
  "interface_exploration",
  "interface_responsiveness",
  "user_communication",
  "personal_conversation",
  "interface_interaction",
  "interface_sensitivity"
)
```

## Helper Functions

```{r helpers}
extract_condition_number <- function(condition_id) {
  if (is.na(condition_id) || !nzchar(as.character(condition_id))) {
    return(NA_real_)
  }

  raw <- sub(".*condition_([0-9]+).*", "\\1", as.character(condition_id), perl = TRUE)
  if (!grepl("^[0-9]+$", raw)) {
    return(NA_real_)
  }

  suppressWarnings(as.numeric(raw))
}

map_interaction_group <- function(condition_number) {
  key <- as.character(suppressWarnings(as.integer(condition_number)))
  if (is.na(condition_number) || !(key %in% names(INTERACTION_CONDITION_LABELS))) {
    return("Other")
  }
  INTERACTION_CONDITION_LABELS[[key]]
}

map_visualization_group <- function(condition_number, visualization_technique, condition_id, condition_name) {
  cn <- suppressWarnings(as.integer(condition_number))
  if (!is.na(cn) && cn == BASELINE_CONDITION_NUMBER) {
    return("Baseline")
  }

  technique_raw <- tolower(trimws(ifelse(is.na(visualization_technique), "", visualization_technique)))
  if (technique_raw == "baseline") {
    return("Baseline")
  }
  if (technique_raw == "confidence_interval") {
    return("PI")
  }
  if (technique_raw == "ensemble_plot") {
    return("Ensemble")
  }
  if (technique_raw == "combined_plot") {
    return("PI + Ensemble")
  }

  condition_id_raw <- tolower(trimws(ifelse(is.na(condition_id), "", condition_id)))
  if (grepl("_ci$", condition_id_raw)) {
    return("PI")
  }
  if (grepl("_ep$", condition_id_raw)) {
    return("Ensemble")
  }
  if (grepl("_ciep$", condition_id_raw)) {
    return("PI + Ensemble")
  }

  condition_name_raw <- tolower(trimws(ifelse(is.na(condition_name), "", condition_name)))
  if (grepl("baseline", condition_name_raw)) {
    return("Baseline")
  }
  if (grepl("combined", condition_name_raw)) {
    return("PI + Ensemble")
  }
  if (grepl("ensemble", condition_name_raw)) {
    return("Ensemble")
  }
  if (grepl("\\(ci\\)|confidence", condition_name_raw)) {
    return("PI")
  }

  "Other"
}

parse_response_json <- function(value) {
  if (is.na(value) || !nzchar(as.character(value))) {
    return(list())
  }

  parsed <- tryCatch(
    jsonlite::fromJSON(as.character(value), simplifyVector = TRUE),
    error = function(e) list()
  )

  if (is.null(parsed) || !is.list(parsed)) {
    return(list())
  }

  parsed
}

expand_response_columns <- function(data, response_col = "response") {
  if (!(response_col %in% names(data))) {
    return(data)
  }

  parsed <- lapply(data[[response_col]], parse_response_json)
  all_keys <- unique(unlist(lapply(parsed, names), use.names = FALSE))
  all_keys <- all_keys[!is.na(all_keys) & nzchar(all_keys)]

  out <- data

  for (key in all_keys) {
    extracted <- vapply(
      parsed,
      function(item) {
        value <- item[[key]]
        if (is.null(value) || length(value) == 0) {
          return(NA_character_)
        }
        as.character(value[[1]])
      },
      character(1)
    )

    if (key %in% names(out)) {
      existing <- out[[key]]
      fill_idx <- is.na(existing) | trimws(as.character(existing)) == ""
      existing[fill_idx] <- extracted[fill_idx]
      out[[key]] <- existing
    } else {
      out[[key]] <- extracted
    }
  }

  out
}

normalize_likert_0_6_to_1_7 <- function(values) {
  numeric_values <- suppressWarnings(as.numeric(values))
  valid <- numeric_values[!is.na(numeric_values)]

  if (length(valid) == 0) {
    return(numeric_values)
  }

  if (all(valid >= 0 & valid <= 6)) {
    return(pmin(pmax(numeric_values + 1, 1), 7))
  }

  numeric_values
}

set_sum_contrasts <- function(data, factors) {
  out <- data
  for (factor_name in factors) {
    out[[factor_name]] <- factor(out[[factor_name]])
    contrasts(out[[factor_name]]) <- contr.sum(length(levels(out[[factor_name]])))
  }
  out
}

identify_attention_check_failures <- function(data) {
  if (!all(c("trial_type", "participant_id") %in% names(data))) {
    return(character(0))
  }

  survey_rows <- data %>%
    dplyr::filter(trial_type == "trust-survey") %>%
    expand_response_columns("response")

  if (nrow(survey_rows) == 0) {
    return(character(0))
  }

  for (key in c(TRUST_ITEM_KEYS, INTERACTION_ITEM_KEYS)) {
    if (!(key %in% names(survey_rows))) {
      survey_rows[[key]] <- NA_real_
    }
    survey_rows[[key]] <- normalize_likert_0_6_to_1_7(survey_rows[[key]])
  }

  trust_complete <- rowSums(!is.na(survey_rows[, TRUST_ITEM_KEYS, drop = FALSE])) == length(TRUST_ITEM_KEYS)
  interaction_complete <- rowSums(!is.na(survey_rows[, INTERACTION_ITEM_KEYS, drop = FALSE])) == length(INTERACTION_ITEM_KEYS)

  trust_uniform <- apply(survey_rows[, TRUST_ITEM_KEYS, drop = FALSE], 1, function(x) {
    length(unique(stats::na.omit(x))) == 1
  })

  interaction_uniform <- apply(survey_rows[, INTERACTION_ITEM_KEYS, drop = FALSE], 1, function(x) {
    length(unique(stats::na.omit(x))) == 1
  })

  failed <- survey_rows$participant_id[trust_complete & interaction_complete & trust_uniform & interaction_uniform]
  unique(as.character(failed[!is.na(failed)]))
}

map_interaction_factor <- function(condition_number) {
  dplyr::case_when(
    condition_number %in% c(21, 22) ~ "hover",
    condition_number %in% c(23, 24) ~ "click",
    condition_number %in% c(25, 26) ~ "animation",
    TRUE ~ NA_character_
  )
}

map_detail_factor <- function(condition_number) {
  dplyr::case_when(
    condition_number %in% c(21, 23, 25) ~ "show_one",
    condition_number %in% c(22, 24, 26) ~ "show_all",
    TRUE ~ NA_character_
  )
}

map_vis_type <- function(visualization_group) {
  dplyr::case_when(
    visualization_group == "PI" ~ "CI",
    visualization_group == "Ensemble" ~ "EP",
    visualization_group == "PI + Ensemble" ~ "CIEP",
    TRUE ~ NA_character_
  )
}

read_participant_csv <- function(file_path) {
  df <- read.csv(file_path, stringsAsFactors = FALSE, check.names = FALSE)
  df$source_file <- basename(file_path)

  if (!("participant_id" %in% names(df)) || all(is.na(df$participant_id))) {
    token <- strsplit(tools::file_path_sans_ext(basename(file_path)), "_")[[1]]
    inferred_id <- ifelse(length(token) >= 2, token[[2]], NA_character_)
    df$participant_id <- inferred_id
  }

  if (!("condition_id" %in% names(df))) {
    df$condition_id <- NA_character_
  }
  if (!("condition_name" %in% names(df))) {
    df$condition_name <- NA_character_
  }

  df$condition_number <- vapply(df$condition_id, extract_condition_number, numeric(1))
  df$interaction_group <- vapply(df$condition_number, map_interaction_group, character(1))
  df$visualization_group <- mapply(
    map_visualization_group,
    condition_number = df$condition_number,
    visualization_technique = if ("visualization_technique" %in% names(df)) df$visualization_technique else NA_character_,
    condition_id = df$condition_id,
    condition_name = df$condition_name,
    USE.NAMES = FALSE
  )

  df
}
```

## Load and Filter Data

```{r load-data}
csv_files <- unlist(
  lapply(
    data_dirs,
    function(dir_path) {
      list.files(dir_path, pattern = params$csv_pattern, full.names = TRUE)
    }
  ),
  use.names = FALSE
)

if (length(csv_files) == 0) {
  stop(
    "No CSV files found in: ",
    paste(data_dirs, collapse = ", "),
    " with pattern ",
    params$csv_pattern
  )
}

combined_data <- dplyr::bind_rows(lapply(csv_files, read_participant_csv))

before_n <- dplyr::n_distinct(combined_data$participant_id)

combined_data <- combined_data %>%
  dplyr::filter(!is.na(participant_id)) %>%
  dplyr::filter(tolower(as.character(participant_id)) != "test")

attention_failures <- identify_attention_check_failures(combined_data)

if (length(attention_failures) > 0) {
  combined_data <- combined_data %>%
    dplyr::filter(!(as.character(participant_id) %in% attention_failures))
}

after_n <- dplyr::n_distinct(combined_data$participant_id)

cat("Data directories:\n")
cat(paste0("  - ", data_dirs), sep = "\n")
cat("\nCSV files loaded: ", length(csv_files), "\n", sep = "")
cat("Participants: ", before_n, " -> ", after_n, "\n", sep = "")
cat("Attention-check exclusions: ", length(attention_failures), "\n", sep = "")
```

## Trust-Survey Preprocessing

```{r preprocess-trust-survey}
trust_survey <- combined_data %>%
  dplyr::filter(trial_type == "trust-survey") %>%
  expand_response_columns("response")

for (key in c(TRUST_ITEM_KEYS, INTERACTION_ITEM_KEYS)) {
  if (!(key %in% names(trust_survey))) {
    trust_survey[[key]] <- NA_real_
  }
  trust_survey[[key]] <- normalize_likert_0_6_to_1_7(trust_survey[[key]])
}

trust_survey <- trust_survey %>%
  dplyr::mutate(
    skeptical_rating_rev = 8 - as.numeric(skeptical_rating),
    usability_difficulty_rev = 8 - as.numeric(usability_difficulty),
    composite_trust_score = rowMeans(
      cbind(
        skeptical_rating_rev,
        as.numeric(data_trust),
        usability_difficulty_rev,
        as.numeric(comprehension_ease)
      ),
      na.rm = TRUE
    ),
    interaction_experience = rowMeans(
      dplyr::across(dplyr::all_of(INTERACTION_ITEM_KEYS)),
      na.rm = TRUE
    ),
    interaction = map_interaction_factor(condition_number),
    detail_presentation = map_detail_factor(condition_number),
    vis_type = map_vis_type(visualization_group),
    interaction_group = vapply(condition_number, map_interaction_group, character(1))
  )

trust_survey$composite_trust_score[is.nan(trust_survey$composite_trust_score)] <- NA_real_
trust_survey$interaction_experience[is.nan(trust_survey$interaction_experience)] <- NA_real_

model_input_raw <- trust_survey %>%
  dplyr::filter(condition_number %in% TREATMENT_CONDITIONS) %>%
  dplyr::filter(
    !is.na(interaction),
    !is.na(detail_presentation),
    !is.na(vis_type),
    !is.na(composite_trust_score),
    !is.na(interaction_experience)
  )

# Aggregate if duplicate rows exist for a participant x condition cell.
model_input <- model_input_raw %>%
  dplyr::group_by(participant_id, vis_type, interaction, detail_presentation) %>%
  dplyr::summarise(
    composite_trust_score = mean(composite_trust_score, na.rm = TRUE),
    interaction_experience = mean(interaction_experience, na.rm = TRUE),
    .groups = "drop"
  )

# Complete within-subject grid for interaction (3) x detail_presentation (2) = 6 cells.
participant_cell_counts <- model_input %>%
  dplyr::count(participant_id, name = "n_cells")

complete_participants <- participant_cell_counts %>%
  dplyr::filter(n_cells == 6) %>%
  dplyr::pull(participant_id)

model_data <- model_input %>%
  dplyr::filter(participant_id %in% complete_participants) %>%
  dplyr::mutate(
    participant_id = factor(participant_id),
    interaction = factor(interaction, levels = c("hover", "click", "animation")),
    detail_presentation = factor(detail_presentation, levels = c("show_one", "show_all")),
    vis_type = factor(vis_type, levels = c("CI", "EP", "CIEP"))
  )

cat("Trust-survey rows (raw): ", nrow(trust_survey), "\n", sep = "")
cat("Model rows after filtering: ", nrow(model_data), "\n", sep = "")
cat("Model participants (complete 6-cell within-subject grid): ", dplyr::n_distinct(model_data$participant_id), "\n", sep = "")
```

## Section 7: Cross-Interaction Technique Summary

```{r section-7-summary}
section7_summary <- model_data %>%
  dplyr::group_by(interaction, detail_presentation) %>%
  dplyr::summarise(
    n = dplyr::n(),
    trust_mean = mean(composite_trust_score, na.rm = TRUE),
    trust_sd = stats::sd(composite_trust_score, na.rm = TRUE),
    trust_se = trust_sd / sqrt(n),
    interaction_mean = mean(interaction_experience, na.rm = TRUE),
    interaction_sd = stats::sd(interaction_experience, na.rm = TRUE),
    interaction_se = interaction_sd / sqrt(n),
    .groups = "drop"
  ) %>%
  dplyr::arrange(interaction, detail_presentation)

knitr::kable(section7_summary, digits = 3, caption = "Section 7 summary by interaction x detail presentation")
```

## Section 8: Interaction x Visualization Grid Summary

```{r section-8-summary}
section8_summary <- model_data %>%
  dplyr::group_by(vis_type, interaction, detail_presentation) %>%
  dplyr::summarise(
    n = dplyr::n(),
    trust_mean = mean(composite_trust_score, na.rm = TRUE),
    trust_sd = stats::sd(composite_trust_score, na.rm = TRUE),
    trust_se = trust_sd / sqrt(n),
    interaction_mean = mean(interaction_experience, na.rm = TRUE),
    interaction_sd = stats::sd(interaction_experience, na.rm = TRUE),
    interaction_se = interaction_sd / sqrt(n),
    .groups = "drop"
  ) %>%
  dplyr::arrange(vis_type, interaction, detail_presentation)

knitr::kable(section8_summary, digits = 3, caption = "Section 8 summary by vis_type x interaction condition")
```

## Regression 1: Trust

```{r regression-trust}
regression_model_data <- set_sum_contrasts(
  model_data,
  factors = c("vis_type", "interaction", "detail_presentation")
)

trust_lm <- lm(
  composite_trust_score ~ vis_type + interaction + detail_presentation,
  data = regression_model_data,
  na.action = na.exclude
)

trust_anova <- anova(trust_lm)
trust_anova
```

## Regression 1: Trust (Joint Effects)

```{r regression-trust-joint-effects}
trust_joint_lm <- lm(
  composite_trust_score ~ vis_type * interaction * detail_presentation,
  data = regression_model_data,
  na.action = na.exclude
)

trust_joint_anova <- anova(trust_joint_lm)
trust_joint_anova
```

## Regression 2: Interaction Experience

```{r regression-interaction-experience}
interaction_lm <- lm(
  interaction_experience ~ vis_type + interaction + detail_presentation,
  data = regression_model_data,
  na.action = na.exclude
)

interaction_anova <- anova(interaction_lm)
interaction_anova
```

## Regression 2: Interaction Experience (Joint Effects)

```{r regression-interaction-experience-joint-effects}
interaction_joint_lm <- lm(
  interaction_experience ~ vis_type * interaction * detail_presentation,
  data = regression_model_data,
  na.action = na.exclude
)

interaction_joint_anova <- anova(interaction_joint_lm)
interaction_joint_anova
```

## EMMs: Interaction

```{r emmeans-interaction}
extract_emmean_with_sd <- function(model, factor_name, sd_data, value_col) {
  emmean_tbl <- emmeans::emmeans(
    model,
    specs = stats::as.formula(paste0("~ ", factor_name))
  ) %>%
    as.data.frame() %>%
    dplyr::select(dplyr::all_of(factor_name), emmean, SE)

  sd_tbl <- sd_data %>%
    dplyr::group_by(.data[[factor_name]]) %>%
    dplyr::summarise(
      sd = stats::sd(.data[[value_col]], na.rm = TRUE),
      .groups = "drop"
    )

  emmean_tbl %>%
    dplyr::left_join(sd_tbl, by = factor_name)
}

interaction_level_scores <- model_data %>%
  dplyr::group_by(participant_id, interaction) %>%
  dplyr::summarise(
    composite_trust_score = mean(composite_trust_score, na.rm = TRUE),
    interaction_experience = mean(interaction_experience, na.rm = TRUE),
    .groups = "drop"
  )

trust_interaction_emmeans <- extract_emmean_with_sd(
  model = trust_joint_lm,
  factor_name = "interaction",
  sd_data = interaction_level_scores,
  value_col = "composite_trust_score"
)

interactionexp_interaction_emmeans <- extract_emmean_with_sd(
  model = interaction_joint_lm,
  factor_name = "interaction",
  sd_data = interaction_level_scores,
  value_col = "interaction_experience"
)

knitr::kable(trust_interaction_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for interaction (trust)")
knitr::kable(interactionexp_interaction_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for interaction (interaction experience)")
```

## EMMs: Detail Presentation

```{r emmeans-detail-presentation}
detail_level_scores <- model_data %>%
  dplyr::group_by(participant_id, detail_presentation) %>%
  dplyr::summarise(
    composite_trust_score = mean(composite_trust_score, na.rm = TRUE),
    interaction_experience = mean(interaction_experience, na.rm = TRUE),
    .groups = "drop"
  )

trust_detail_emmeans <- extract_emmean_with_sd(
  model = trust_joint_lm,
  factor_name = "detail_presentation",
  sd_data = detail_level_scores,
  value_col = "composite_trust_score"
)

interactionexp_detail_emmeans <- extract_emmean_with_sd(
  model = interaction_joint_lm,
  factor_name = "detail_presentation",
  sd_data = detail_level_scores,
  value_col = "interaction_experience"
)

knitr::kable(trust_detail_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for detail_presentation (trust)")
knitr::kable(interactionexp_detail_emmeans, digits = 4, caption = "EMMs (emmean, SE, SD) for detail_presentation (interaction experience)")
```
