---
title: "Experiment 3 Composite Trust/Interaction Power Analysis"
output:
  html_document: default
  pdf_document: default
params:
  data_dir: "../data/dist 8/data"
  csv_pattern: "^user_.*\\.csv$"
  alpha: 0.05
  power_targets: [0.8, 0.9]
  power_nsim: 3000
  n_min: 6
  n_max: 220
  seed: 20260317
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

```{r table-spacing-style, results='asis', echo=FALSE}
table_column_padding_html <- "2rem"
table_column_padding_latex <- "10pt"

if (knitr::is_html_output()) {
  cat(
    "<style>\n",
    "table th,\n",
    "table td {\n",
    "  padding-left: ", table_column_padding_html, " !important;\n",
    "  padding-right: ", table_column_padding_html, " !important;\n",
    "}\n",
    "</style>\n",
    sep = ""
  )
}

if (knitr::is_latex_output()) {
  cat("\\setlength{\\tabcolsep}{", table_column_padding_latex, "}\n", sep = "")
}
```

## Goal

This report follows the preprocessing in `analysis-0316.ipynb` and estimates participant requirements for the main interaction-condition analysis:

- Four within-participant interaction conditions:
  - `Hover Show One`
  - `Hover Show All`
  - `Click Show One`
  - `Click Show All`
- Outcomes:
  - `composite_trust_score`
  - `composite_interaction_score`
- Scopes:
  - Panel-specific (`PI`, `Ensemble`, `PI + Ensemble`)
  - Combined across visualization groups (`PI + Ensemble + CIEP`)

Power is estimated with simulation for the omnibus repeated-measures ANOVA effect across the four interaction conditions.

## Packages

```{r packages}
library(dplyr)
library(ggplot2)
library(jsonlite)
library(knitr)
library(MASS)
library(tidyr)
```

## Paths

```{r paths}
report_dir <- local({
  current_input <- tryCatch(
    knitr::current_input(),
    error = function(e) character(0)
  )

  if (length(current_input) == 1 && nzchar(current_input)) {
    input_path <- current_input

    if (!grepl("^(/|[A-Za-z]:[/\\\\])", input_path)) {
      input_path <- file.path(getwd(), input_path)
    }

    if (grepl("\\.[Rr]md$", input_path) || file.exists(input_path)) {
      return(normalizePath(dirname(input_path), winslash = "/", mustWork = TRUE))
    }
  }

  current_input_dir <- tryCatch(
    knitr::current_input(dir = TRUE),
    error = function(e) character(0)
  )

  if (length(current_input_dir) == 1 && nzchar(current_input_dir)) {
    if (grepl("\\.[Rr]md$", current_input_dir)) {
      return(normalizePath(dirname(current_input_dir), winslash = "/", mustWork = TRUE))
    }

    if (dir.exists(current_input_dir)) {
      return(normalizePath(current_input_dir, winslash = "/", mustWork = TRUE))
    }
  }

  fallback_dir <- file.path(getwd(), "Experiment3", "analysis")
  normalizePath(fallback_dir, winslash = "/", mustWork = TRUE)
})

resolve_report_path <- function(path_value) {
  if (grepl("^(/|[A-Za-z]:[/\\\\])", path_value)) {
    return(normalizePath(path_value, winslash = "/", mustWork = TRUE))
  }

  normalizePath(
    file.path(report_dir, path_value),
    winslash = "/",
    mustWork = TRUE
  )
}

data_dir <- resolve_report_path(params$data_dir)
```

## Constants

```{r constants}
INTERACTION_CONDITION_LABELS <- c(
  "1" = "Baseline",
  "21" = "Hover Show One",
  "22" = "Hover Show All",
  "23" = "Click Show One",
  "24" = "Click Show All"
)

ROW_ORDER <- c("Hover Show One", "Hover Show All", "Click Show One", "Click Show All")
VIS_LABELS <- c("PI", "Ensemble", "PI + Ensemble")
BASELINE_CONDITION_NUMBER <- 1

INTERACTION_QUESTION_KEYS <- c(
  "navigation_control",
  "content_control",
  "pace_control",
  "interface_exploration",
  "interface_responsiveness",
  "user_communication",
  "personal_conversation",
  "interface_interaction",
  "interface_sensitivity"
)

TRUST_QUESTION_KEYS <- c(
  "skeptical_rating",
  "data_trust",
  "usability_difficulty",
  "comprehension_ease"
)
```

## Helper Functions

```{r helpers}
extract_condition_number <- function(condition_id) {
  if (is.na(condition_id) || !nzchar(as.character(condition_id))) {
    return(NA_real_)
  }

  match <- regexpr("condition_([0-9]+)", as.character(condition_id), perl = TRUE)
  if (match[1] == -1) {
    return(NA_real_)
  }

  value <- sub(".*condition_([0-9]+).*", "\\1", as.character(condition_id), perl = TRUE)
  suppressWarnings(as.numeric(value))
}

map_interaction_group <- function(condition_number) {
  key <- as.character(suppressWarnings(as.integer(condition_number)))
  if (is.na(condition_number) || !(key %in% names(INTERACTION_CONDITION_LABELS))) {
    return("Other")
  }
  INTERACTION_CONDITION_LABELS[[key]]
}

map_visualization_group <- function(condition_number, visualization_technique, condition_id, condition_name) {
  cn <- suppressWarnings(as.integer(condition_number))
  if (!is.na(cn) && cn == BASELINE_CONDITION_NUMBER) {
    return("Baseline")
  }

  technique_raw <- tolower(trimws(ifelse(is.na(visualization_technique), "", visualization_technique)))
  if (technique_raw == "baseline") {
    return("Baseline")
  }
  if (technique_raw == "confidence_interval") {
    return("PI")
  }
  if (technique_raw == "ensemble_plot") {
    return("Ensemble")
  }
  if (technique_raw == "combined_plot") {
    return("PI + Ensemble")
  }

  condition_id_raw <- tolower(trimws(ifelse(is.na(condition_id), "", condition_id)))
  if (grepl("_ci$", condition_id_raw)) {
    return("PI")
  }
  if (grepl("_ep$", condition_id_raw)) {
    return("Ensemble")
  }
  if (grepl("_ciep$", condition_id_raw)) {
    return("PI + Ensemble")
  }

  condition_name_raw <- tolower(trimws(ifelse(is.na(condition_name), "", condition_name)))
  if (grepl("baseline", condition_name_raw)) {
    return("Baseline")
  }
  if (grepl("combined", condition_name_raw)) {
    return("PI + Ensemble")
  }
  if (grepl("ensemble", condition_name_raw)) {
    return("Ensemble")
  }
  if (grepl("\\(ci\\)|confidence", condition_name_raw)) {
    return("PI")
  }

  "Other"
}

parse_response_json <- function(value) {
  if (is.na(value) || !nzchar(as.character(value))) {
    return(list())
  }

  parsed <- tryCatch(
    fromJSON(as.character(value), simplifyVector = TRUE),
    error = function(e) list()
  )

  if (is.null(parsed) || !is.list(parsed)) {
    return(list())
  }

  parsed
}

normalize_likert_0_6_to_1_7 <- function(values) {
  numeric_values <- suppressWarnings(as.numeric(values))
  valid <- numeric_values[!is.na(numeric_values)]

  if (length(valid) == 0) {
    return(numeric_values)
  }

  if (all(valid >= 0 & valid <= 6)) {
    return(numeric_values + 1)
  }

  numeric_values
}

ensure_likert_columns <- function(data, keys) {
  if (nrow(data) == 0) {
    return(data)
  }

  working <- data
  parsed <- if ("response" %in% names(working)) {
    lapply(working$response, parse_response_json)
  } else {
    replicate(nrow(working), list(), simplify = FALSE)
  }

  for (key in keys) {
    existing <- if (key %in% names(working)) {
      suppressWarnings(as.numeric(working[[key]]))
    } else {
      rep(NA_real_, nrow(working))
    }

    if (!(key %in% names(working)) || sum(!is.na(existing)) == 0) {
      extracted_raw <- vapply(
        parsed,
        function(x) {
          value <- x[[key]]
          if (is.null(value) || length(value) == 0) {
            return(NA_character_)
          }
          as.character(value[[1]])
        },
        character(1)
      )

      extracted <- normalize_likert_0_6_to_1_7(extracted_raw)
      working[[key]] <- extracted
    } else {
      working[[key]] <- existing
    }
  }

  working
}

compute_composite_scores <- function(data) {
  if (is.null(data) || nrow(data) == 0) {
    return(data.frame())
  }

  working <- data

  all_keys <- c(TRUST_QUESTION_KEYS, INTERACTION_QUESTION_KEYS)
  for (col in all_keys) {
    if (col %in% names(working)) {
      working[[col]] <- suppressWarnings(as.numeric(working[[col]]))
    }
  }

  trust_required <- c("skeptical_rating", "data_trust", "usability_difficulty", "comprehension_ease")
  if (all(trust_required %in% names(working))) {
    working$skeptical_rating_rev <- 8 - working$skeptical_rating
    working$usability_difficulty_rev <- 8 - working$usability_difficulty
    working$composite_trust_score <- rowMeans(
      cbind(
        working$skeptical_rating_rev,
        working$data_trust,
        working$usability_difficulty_rev,
        working$comprehension_ease
      ),
      na.rm = TRUE
    )
  }

  interaction_available <- INTERACTION_QUESTION_KEYS[INTERACTION_QUESTION_KEYS %in% names(working)]
  if (length(interaction_available) > 0) {
    working$composite_interaction_score <- rowMeans(
      as.matrix(working[, interaction_available, drop = FALSE]),
      na.rm = TRUE
    )
  }

  working
}

load_participant_data <- function(file_path) {
  df <- read.csv(file_path, stringsAsFactors = FALSE)
  df$source_file <- basename(file_path)

  if (!"participant_id" %in% names(df) || all(is.na(df$participant_id))) {
    pieces <- strsplit(tools::file_path_sans_ext(basename(file_path)), "_")[[1]]
    participant_guess <- if (length(pieces) >= 2) pieces[[2]] else basename(file_path)
    df$participant_id <- participant_guess
  }

  if (!"condition_id" %in% names(df)) {
    df$condition_id <- NA_character_
  }
  if (!"condition_name" %in% names(df)) {
    df$condition_name <- NA_character_
  }
  if (!"visualization_technique" %in% names(df)) {
    df$visualization_technique <- NA_character_
  }

  df$condition_number <- vapply(df$condition_id, extract_condition_number, numeric(1))
  df$interaction_group <- vapply(df$condition_number, map_interaction_group, character(1))
  df$visualization_group <- mapply(
    map_visualization_group,
    condition_number = df$condition_number,
    visualization_technique = df$visualization_technique,
    condition_id = df$condition_id,
    condition_name = df$condition_name,
    USE.NAMES = FALSE
  )

  df
}

complete_case_matrix <- function(data, value_col, vis_label = NULL) {
  working <- data %>%
    filter(interaction_group %in% ROW_ORDER)

  if (!is.null(vis_label) && !is.na(vis_label)) {
    working <- working %>% filter(visualization_group == vis_label)
  }

  if (!(value_col %in% names(working))) {
    return(matrix(numeric(0), nrow = 0, ncol = length(ROW_ORDER)))
  }

  working[[value_col]] <- suppressWarnings(as.numeric(working[[value_col]]))
  working <- working %>%
    filter(!is.na(participant_id), !is.na(interaction_group), !is.na(.data[[value_col]]))

  complete_ids <- working %>%
    group_by(participant_id) %>%
    summarise(k = n_distinct(interaction_group), .groups = "drop") %>%
    filter(k >= length(ROW_ORDER)) %>%
    pull(participant_id)

  if (length(complete_ids) == 0) {
    return(matrix(numeric(0), nrow = 0, ncol = length(ROW_ORDER)))
  }

  wide <- working %>%
    filter(participant_id %in% complete_ids) %>%
    group_by(participant_id, interaction_group) %>%
    summarise(value = mean(.data[[value_col]], na.rm = TRUE), .groups = "drop") %>%
    mutate(interaction_group = factor(interaction_group, levels = ROW_ORDER)) %>%
    tidyr::pivot_wider(names_from = interaction_group, values_from = value) %>%
    arrange(participant_id)

  if (nrow(wide) == 0) {
    return(matrix(numeric(0), nrow = 0, ncol = length(ROW_ORDER)))
  }

  mat <- as.matrix(wide[, ROW_ORDER, drop = FALSE])
  storage.mode(mat) <- "double"
  mat <- mat[stats::complete.cases(mat), , drop = FALSE]
  colnames(mat) <- ROW_ORDER
  mat
}

nearest_pd <- function(sigma_matrix, tol = 1e-6) {
  sym <- (sigma_matrix + t(sigma_matrix)) / 2
  eig <- eigen(sym)
  eig$values[eig$values < tol] <- tol
  pd <- eig$vectors %*% diag(eig$values) %*% t(eig$vectors)
  pd <- (pd + t(pd)) / 2
  diag(pd) <- pmax(diag(pd), tol)
  pd
}

rm_anova_stats <- function(y_matrix) {
  n <- nrow(y_matrix)
  k <- ncol(y_matrix)

  if (n < 2 || k < 2) {
    return(list(F = NA_real_, p = NA_real_, eta_p2 = NA_real_, cohen_f = NA_real_))
  }

  grand_mean <- mean(y_matrix)
  condition_means <- colMeans(y_matrix)
  subject_means <- rowMeans(y_matrix)

  ss_condition <- n * sum((condition_means - grand_mean)^2)
  ss_subject <- k * sum((subject_means - grand_mean)^2)
  ss_total <- sum((y_matrix - grand_mean)^2)
  ss_error <- ss_total - ss_condition - ss_subject

  df1 <- k - 1
  df2 <- (n - 1) * (k - 1)

  if (!is.finite(ss_error) || ss_error <= 0) {
    return(list(F = Inf, p = 0, eta_p2 = 1, cohen_f = Inf))
  }

  ms_condition <- ss_condition / df1
  ms_error <- ss_error / df2
  f_value <- ms_condition / ms_error
  p_value <- pf(f_value, df1 = df1, df2 = df2, lower.tail = FALSE)
  eta_p2 <- (f_value * df1) / (f_value * df1 + df2)
  cohen_f <- sqrt(eta_p2 / (1 - eta_p2))

  list(F = f_value, p = p_value, eta_p2 = eta_p2, cohen_f = cohen_f)
}

estimate_power_at_n <- function(mu, sigma_matrix, n_participants, alpha, nsim, seed) {
  set.seed(seed + n_participants)
  hits <- logical(nsim)

  for (i in seq_len(nsim)) {
    sim <- MASS::mvrnorm(n = n_participants, mu = mu, Sigma = sigma_matrix)
    sim_stats <- rm_anova_stats(sim)
    hits[[i]] <- is.finite(sim_stats$p) && !is.na(sim_stats$p) && (sim_stats$p < alpha)
  }

  mean(hits)
}

find_required_n <- function(mu, sigma_matrix, target_power, alpha, nsim, n_min, n_max, seed) {
  cache <- new.env(parent = emptyenv())
  evaluated_ns <- integer(0)

  power_at <- function(n_value) {
    key <- as.character(n_value)
    if (!exists(key, envir = cache, inherits = FALSE)) {
      value <- estimate_power_at_n(
        mu = mu,
        sigma_matrix = sigma_matrix,
        n_participants = n_value,
        alpha = alpha,
        nsim = nsim,
        seed = seed
      )
      assign(key, value, envir = cache)
      evaluated_ns <<- c(evaluated_ns, n_value)
    }
    get(key, envir = cache, inherits = FALSE)
  }

  lo <- n_min
  hi <- n_min

  if (power_at(lo) >= target_power) {
    required <- lo
  } else {
    required <- NA_real_
    while (hi < n_max && power_at(hi) < target_power) {
      hi <- min(n_max, ceiling(hi * 1.5))
      if (hi <= lo) {
        hi <- min(n_max, lo + 1)
      }
      lo <- hi
    }

    if (power_at(hi) >= target_power) {
      left <- n_min
      right <- hi
      while (left < right) {
        mid <- floor((left + right) / 2)
        if (power_at(mid) >= target_power) {
          right <- mid
        } else {
          left <- mid + 1
        }
      }
      required <- left
    }
  }

  unique_ns <- sort(unique(evaluated_ns))
  evaluated <- data.frame(
    n_participants = unique_ns,
    power = vapply(unique_ns, power_at, numeric(1)),
    target_power = target_power
  )

  list(required_n = required, evaluated = evaluated)
}

summarize_one_analysis <- function(data, scope_label, vis_label, value_col, outcome_label, base_seed) {
  mat <- complete_case_matrix(data, value_col = value_col, vis_label = vis_label)

  if (nrow(mat) < 5) {
    empty_trace <- data.frame(
      scope = character(0),
      outcome = character(0),
      target_power = numeric(0),
      n_participants = numeric(0),
      power = numeric(0)
    )
    return(list(
      summary = data.frame(
        scope = scope_label,
        outcome = outcome_label,
        usable_n = nrow(mat),
        pilot_F = NA_real_,
        pilot_p = NA_real_,
        pilot_eta_p2 = NA_real_,
        pilot_f = NA_real_,
        required_n_80 = NA_real_,
        required_n_90 = NA_real_
      ),
      trace = empty_trace
    ))
  }

  pilot <- rm_anova_stats(mat)

  sigma_matrix <- stats::cov(mat)
  if (!all(dim(sigma_matrix) == c(ncol(mat), ncol(mat)))) {
    sigma_matrix <- diag(stats::var(as.numeric(mat)), ncol(mat))
  }
  sigma_matrix <- nearest_pd(sigma_matrix)
  mu <- colMeans(mat)

  target_80 <- if (0.8 %in% params$power_targets) 0.8 else params$power_targets[[1]]
  target_90 <- if (0.9 %in% params$power_targets) 0.9 else tail(params$power_targets, 1)

  req_80 <- find_required_n(
    mu = mu,
    sigma_matrix = sigma_matrix,
    target_power = target_80,
    alpha = params$alpha,
    nsim = params$power_nsim,
    n_min = params$n_min,
    n_max = params$n_max,
    seed = base_seed
  )

  req_90 <- find_required_n(
    mu = mu,
    sigma_matrix = sigma_matrix,
    target_power = target_90,
    alpha = params$alpha,
    nsim = params$power_nsim,
    n_min = params$n_min,
    n_max = params$n_max,
    seed = base_seed + 1000
  )

  summary_row <- data.frame(
    scope = scope_label,
    outcome = outcome_label,
    usable_n = nrow(mat),
    pilot_F = pilot$F,
    pilot_p = pilot$p,
    pilot_eta_p2 = pilot$eta_p2,
    pilot_f = pilot$cohen_f,
    required_n_80 = req_80$required_n,
    required_n_90 = req_90$required_n
  )

  trace <- bind_rows(
    req_80$evaluated,
    req_90$evaluated
  ) %>%
    distinct(target_power, n_participants, .keep_all = TRUE) %>%
    mutate(
      scope = scope_label,
      outcome = outcome_label
    ) %>%
    dplyr::select(scope, outcome, target_power, n_participants, power)

  list(summary = summary_row, trace = trace)
}
```

## Load Experiment 3 Data

```{r load-data}
csv_files <- sort(list.files(
  data_dir,
  pattern = params$csv_pattern,
  full.names = TRUE
))

if (length(csv_files) == 0) {
  stop("No participant CSV files found in: ", data_dir)
}

combined_data <- bind_rows(lapply(csv_files, load_participant_data)) %>%
  filter(!is.na(participant_id)) %>%
  filter(tolower(as.character(participant_id)) != "test")

relevant_trial_types <- c(
  "prediction-task",
  "vis-literacy",
  "trust-survey",
  "interaction-feedback",
  "personality-survey",
  "survey-text",
  "survey-multi-choice"
)

relevant_trials <- combined_data %>%
  filter(trial_type %in% relevant_trial_types)

trust_survey_rows <- relevant_trials %>%
  filter(trial_type == "trust-survey")

trust_survey_expanded <- ensure_likert_columns(
  trust_survey_rows,
  c(TRUST_QUESTION_KEYS, INTERACTION_QUESTION_KEYS)
)

composite_source <- compute_composite_scores(trust_survey_expanded)

raw_composite_treatment <- composite_source %>%
  filter(condition_number %in% c(21, 22, 23, 24)) %>%
  filter(interaction_group %in% ROW_ORDER)

overview <- data.frame(
  metric = c(
    "Participant CSV files",
    "Participants (non-test)",
    "Trust-survey rows",
    "Treatment trust rows (conditions 21/22/23/24)"
  ),
  value = c(
    length(csv_files),
    dplyr::n_distinct(combined_data$participant_id),
    nrow(trust_survey_rows),
    nrow(raw_composite_treatment)
  )
)

kable(overview, align = c("l", "r"))
```

## Coverage and Complete Cases

```{r coverage}
assigned_counts <- raw_composite_treatment %>%
  filter(visualization_group %in% VIS_LABELS) %>%
  distinct(participant_id, visualization_group) %>%
  count(visualization_group, name = "assigned_n") %>%
  complete(visualization_group = VIS_LABELS, fill = list(assigned_n = 0))

complete_counts <- raw_composite_treatment %>%
  filter(visualization_group %in% VIS_LABELS) %>%
  group_by(visualization_group, participant_id) %>%
  summarise(k = n_distinct(interaction_group), .groups = "drop") %>%
  filter(k >= length(ROW_ORDER)) %>%
  count(visualization_group, name = "complete_n") %>%
  complete(visualization_group = VIS_LABELS, fill = list(complete_n = 0))

coverage_table <- assigned_counts %>%
  left_join(complete_counts, by = "visualization_group") %>%
  mutate(completion_rate = ifelse(assigned_n > 0, complete_n / assigned_n, NA_real_))

kable(coverage_table, digits = 3)
```

## Power Analysis

```{r power-analysis}
set.seed(params$seed)

analysis_specs <- bind_rows(
  data.frame(scope = VIS_LABELS, vis_label = VIS_LABELS, stringsAsFactors = FALSE),
  data.frame(scope = "Combined", vis_label = NA_character_, stringsAsFactors = FALSE)
)

outcome_specs <- data.frame(
  outcome = c("Trust", "Interaction"),
  value_col = c("composite_trust_score", "composite_interaction_score"),
  stringsAsFactors = FALSE
)

summary_rows <- list()
trace_rows <- list()
row_idx <- 1

for (s in seq_len(nrow(analysis_specs))) {
  for (o in seq_len(nrow(outcome_specs))) {
    result <- summarize_one_analysis(
      data = raw_composite_treatment,
      scope_label = analysis_specs$scope[[s]],
      vis_label = analysis_specs$vis_label[[s]],
      value_col = outcome_specs$value_col[[o]],
      outcome_label = outcome_specs$outcome[[o]],
      base_seed = params$seed + row_idx * 100
    )

    summary_rows[[length(summary_rows) + 1]] <- result$summary
    trace_rows[[length(trace_rows) + 1]] <- result$trace
    row_idx <- row_idx + 1
  }
}

power_summary <- bind_rows(summary_rows) %>%
  arrange(factor(scope, levels = c(VIS_LABELS, "Combined")), outcome)

power_trace <- bind_rows(trace_rows)

kable(power_summary, digits = 3)
```

## Recommended Sample Sizes

```{r recommendations}
panel_summary <- power_summary %>%
  filter(scope %in% VIS_LABELS)

recommended_panel_80 <- suppressWarnings(max(panel_summary$required_n_80, na.rm = TRUE))
recommended_panel_90 <- suppressWarnings(max(panel_summary$required_n_90, na.rm = TRUE))

if (!is.finite(recommended_panel_80)) {
  recommended_panel_80 <- NA_real_
}
if (!is.finite(recommended_panel_90)) {
  recommended_panel_90 <- NA_real_
}

combined_summary <- power_summary %>%
  filter(scope == "Combined")

recommendation_table <- data.frame(
  analysis_target = c(
    "Panel-specific (power all 3 visualization panels and both outcomes)",
    "Combined-only Trust",
    "Combined-only Interaction"
  ),
  n_for_80_power = c(
    recommended_panel_80,
    combined_summary$required_n_80[combined_summary$outcome == "Trust"],
    combined_summary$required_n_80[combined_summary$outcome == "Interaction"]
  ),
  n_for_90_power = c(
    recommended_panel_90,
    combined_summary$required_n_90[combined_summary$outcome == "Trust"],
    combined_summary$required_n_90[combined_summary$outcome == "Interaction"]
  )
)

kable(recommendation_table, digits = 0)
```

## Power Trace Diagnostics

```{r power-trace-plot, fig.width=9.5, fig.height=6.5}
if (nrow(power_trace) > 0) {
  ggplot(
    power_trace,
    aes(
      x = n_participants,
      y = power,
      color = factor(target_power),
      group = interaction(target_power, scope, outcome)
    )
  ) +
    geom_line(linewidth = 0.9) +
    geom_point(size = 1.8) +
    geom_hline(yintercept = 0.8, linetype = "dashed", color = "gray45") +
    geom_hline(yintercept = 0.9, linetype = "dotted", color = "gray45") +
    facet_grid(outcome ~ scope) +
    scale_y_continuous(limits = c(0, 1)) +
    labs(
      title = "Simulation-Based Power Traces for RM-ANOVA Omnibus Effect",
      x = "Participants",
      y = "Estimated power",
      color = "Target power"
    ) +
    theme_minimal(base_size = 12)
}
```

## Save Outputs

```{r save-outputs}
summary_path <- file.path(report_dir, "power_analysis_0316_r_summary.csv")
trace_path <- file.path(report_dir, "power_analysis_0316_r_trace.csv")
coverage_path <- file.path(report_dir, "power_analysis_0316_r_coverage.csv")

write.csv(power_summary, summary_path, row.names = FALSE)
write.csv(power_trace, trace_path, row.names = FALSE)
write.csv(coverage_table, coverage_path, row.names = FALSE)

data.frame(
  file = c(summary_path, trace_path, coverage_path)
) %>%
  kable()
```
