---
title: "Experiment 2: Trust/Interaction/Confidence ~ Linear Fits on Raw Participant Lines by Interaction Mode (0330, No CI)"
output:
  html_document: default
params:
  data_dir_candidates:
    - "../data/0325/data"
    - "../data/0328/data"
  csv_pattern: "^user_.*\\.csv$"
  seed: 20260330
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(params$seed)
```

## Goal

Recreate Experiment 2 preprocessing (same data sources and no-CI filter) and run only linear regression on raw participant data:

- `Trust ~ number of lines`, separated into `click`, `hover`, `static`
- `Interactive experience ~ number of lines`, separated into `click`, `hover`, `static`
- `Confidence ~ number of lines`, separated into `click`, `hover`, `static`
- Exclude CI condition (`condition 2`) from analysis
- Do not apply within-participant normalization

Output:

- 9 participant-trajectory raw-data plots with linear regression lines (3 outcomes x 3 interaction modes)
- 3 coefficient tables (one per outcome), reporting intercept and slope by interaction mode

## Packages

```{r packages}
required_packages <- c(
  "dplyr",
  "jsonlite",
  "ggplot2",
  "knitr"
)

missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)
]

if (length(missing_packages) > 0) {
  stop(
    "Missing required packages: ",
    paste(missing_packages, collapse = ", "),
    ". Install them before rendering."
  )
}

lapply(required_packages, library, character.only = TRUE)
```

## Paths

```{r paths}
report_dir <- local({
  current_input <- tryCatch(
    knitr::current_input(),
    error = function(e) character(0)
  )

  if (length(current_input) == 1 && nzchar(current_input)) {
    input_path <- current_input

    if (!grepl("^(/|[A-Za-z]:[/\\\\])", input_path)) {
      input_path <- file.path(getwd(), input_path)
    }

    if (grepl("\\.[Rr]md$", input_path) || file.exists(input_path)) {
      return(normalizePath(dirname(input_path), winslash = "/", mustWork = TRUE))
    }
  }

  fallback_dir <- file.path(getwd(), "Experiment2", "analysis")
  normalizePath(fallback_dir, winslash = "/", mustWork = TRUE)
})

resolve_report_path <- function(path_value) {
  if (grepl("^(/|[A-Za-z]:[/\\\\])", path_value)) {
    return(normalizePath(path_value, winslash = "/", mustWork = TRUE))
  }

  normalizePath(
    file.path(report_dir, path_value),
    winslash = "/",
    mustWork = TRUE
  )
}

data_dir_candidates <- vapply(params$data_dir_candidates, resolve_report_path, character(1))
existing_data_dirs <- data_dir_candidates[dir.exists(data_dir_candidates)]

if (length(existing_data_dirs) != length(data_dir_candidates)) {
  missing_dirs <- setdiff(data_dir_candidates, existing_data_dirs)
  stop(
    "Missing required data directory(ies): ",
    paste(missing_dirs, collapse = ", ")
  )
}
```

## Constants

```{r constants}
CONDITION_LABELS <- c(
  "1" = "Baseline",
  "2" = "CI",
  "3" = "2 Lines",
  "4" = "3 Lines",
  "5" = "4 Lines",
  "6" = "5 Lines",
  "7" = "6 Lines",
  "8" = "7 Lines",
  "9" = "8 Lines",
  "10" = "9 Lines"
)

TREATMENT_CONDITION_NUMBERS <- c(3, 4, 5, 6, 7, 8, 9, 10)

TRUST_QUESTION_KEYS <- c(
  "skeptical_rating",
  "data_trust",
  "usability_difficulty",
  "comprehension_ease"
)

INTERACTION_QUESTION_KEYS <- c(
  "navigation_control",
  "content_control",
  "pace_control",
  "interface_exploration",
  "interface_responsiveness",
  "user_communication",
  "personal_conversation",
  "interface_interaction",
  "interface_sensitivity"
)

CONFIDENCE_QUESTION_KEYS <- c("confidence_rating")
```

## Helper Functions

```{r helpers}
extract_condition_number <- function(condition_id) {
  if (is.na(condition_id) || !nzchar(as.character(condition_id))) {
    return(NA_real_)
  }

  raw <- sub(".*condition_([0-9]+).*", "\\1", as.character(condition_id), perl = TRUE)
  if (!grepl("^[0-9]+$", raw)) {
    return(NA_real_)
  }

  as.numeric(raw)
}

map_condition_labels <- function(condition_numbers) {
  vapply(
    condition_numbers,
    function(x) {
      key <- as.character(suppressWarnings(as.integer(x)))
      if (is.na(x) || !(key %in% names(CONDITION_LABELS))) {
        return("Other")
      }
      CONDITION_LABELS[[key]]
    },
    character(1)
  )
}

extract_participant_id_from_filename <- function(file_path) {
  parts <- strsplit(tools::file_path_sans_ext(basename(file_path)), "_", fixed = TRUE)[[1]]
  if (length(parts) >= 2) {
    return(parts[[2]])
  }
  NA_character_
}

parse_response_json <- function(value) {
  if (is.null(value) || length(value) == 0 || is.na(value) || !nzchar(as.character(value))) {
    return(list())
  }

  if (is.list(value) && !is.null(names(value))) {
    return(value)
  }

  parsed <- tryCatch(
    jsonlite::fromJSON(as.character(value), simplifyVector = TRUE),
    error = function(e) NULL
  )

  if (is.null(parsed) || !is.list(parsed)) {
    return(list())
  }

  parsed
}

safe_get_scalar <- function(x) {
  if (is.null(x) || length(x) == 0) {
    return(NA_character_)
  }

  as.character(x[[1]])
}

expand_response_columns <- function(data, response_col = "response") {
  if (!(response_col %in% names(data))) {
    return(data)
  }

  parsed_list <- lapply(data[[response_col]], parse_response_json)
  all_keys <- unique(unlist(lapply(parsed_list, names), use.names = FALSE))

  if (length(all_keys) == 0) {
    return(data)
  }

  expanded <- data.frame(
    lapply(all_keys, function(key) {
      vapply(parsed_list, function(item) safe_get_scalar(item[[key]]), character(1))
    }),
    stringsAsFactors = FALSE,
    check.names = FALSE
  )
  names(expanded) <- all_keys

  merged <- data
  for (col in names(expanded)) {
    parsed_values <- expanded[[col]]

    if (col %in% names(merged)) {
      existing <- merged[[col]]
      existing_chr <- trimws(as.character(existing))
      fill_mask <- is.na(existing) | existing_chr == ""
      existing[fill_mask] <- parsed_values[fill_mask]
      merged[[col]] <- existing
    } else {
      merged[[col]] <- parsed_values
    }
  }

  merged
}

identify_attention_check_failures <- function(
  data,
  trust_keys = TRUST_QUESTION_KEYS,
  interaction_keys = INTERACTION_QUESTION_KEYS,
  survey_trial_type = "trust-survey"
) {
  empty_result <- list(ids = character(0), details = data.frame())

  if (is.null(data) || nrow(data) == 0) {
    return(empty_result)
  }

  if (!all(c("trial_type", "participant_id") %in% names(data))) {
    return(empty_result)
  }

  survey_rows <- data[data$trial_type == survey_trial_type, , drop = FALSE]
  if (nrow(survey_rows) == 0) {
    return(empty_result)
  }

  survey_rows <- expand_response_columns(survey_rows)
  parsed_response <- if ("response" %in% names(survey_rows)) {
    lapply(survey_rows$response, parse_response_json)
  } else {
    replicate(nrow(survey_rows), list(), simplify = FALSE)
  }

  for (key in c(trust_keys, interaction_keys)) {
    existing <- if (key %in% names(survey_rows)) {
      suppressWarnings(as.numeric(survey_rows[[key]]))
    } else {
      rep(NA_real_, nrow(survey_rows))
    }

    if (sum(!is.na(existing)) == 0) {
      extracted <- vapply(parsed_response, function(item) safe_get_scalar(item[[key]]), character(1))
      existing <- suppressWarnings(as.numeric(extracted))
    }

    survey_rows[[key]] <- existing
  }

  trust_complete <- rowSums(is.na(survey_rows[, trust_keys, drop = FALSE])) == 0
  interaction_complete <- rowSums(is.na(survey_rows[, interaction_keys, drop = FALSE])) == 0

  trust_uniform <- apply(
    survey_rows[, trust_keys, drop = FALSE],
    1,
    function(row) {
      values <- unique(row[!is.na(row)])
      length(values) == 1
    }
  )

  interaction_uniform <- apply(
    survey_rows[, interaction_keys, drop = FALSE],
    1,
    function(row) {
      values <- unique(row[!is.na(row)])
      length(values) == 1
    }
  )

  failure_mask <- trust_complete & interaction_complete & trust_uniform & interaction_uniform
  failure_rows <- survey_rows[failure_mask & !is.na(survey_rows$participant_id), , drop = FALSE]

  if (nrow(failure_rows) == 0) {
    return(empty_result)
  }

  failure_rows$participant_id <- as.character(failure_rows$participant_id)
  detail_columns <- c(
    "participant_id",
    "condition_id",
    "condition_number",
    trust_keys,
    interaction_keys
  )
  available_detail_columns <- detail_columns[detail_columns %in% names(failure_rows)]

  list(
    ids = unique(failure_rows$participant_id),
    details = failure_rows[, available_detail_columns, drop = FALSE]
  )
}

ensure_likert_columns <- function(data, keys) {
  if (is.null(data) || nrow(data) == 0) {
    return(data)
  }

  working <- data
  parsed <- if ("response" %in% names(working)) {
    lapply(working$response, parse_response_json)
  } else {
    replicate(nrow(working), list(), simplify = FALSE)
  }

  for (key in keys) {
    existing <- if (key %in% names(working)) {
      suppressWarnings(as.numeric(working[[key]]))
    } else {
      rep(NA_real_, nrow(working))
    }

    if (!(key %in% names(working)) || sum(!is.na(existing)) == 0) {
      extracted <- suppressWarnings(as.numeric(
        vapply(parsed, function(item) safe_get_scalar(item[[key]]), character(1))
      ))

      valid <- extracted[!is.na(extracted)]
      if (length(valid) > 0 && all(valid >= 0 & valid <= 6)) {
        extracted <- extracted + 1
      }

      working[[key]] <- extracted
    } else {
      working[[key]] <- existing
    }
  }

  working
}

compute_composite_scores <- function(data) {
  if (is.null(data) || nrow(data) == 0) {
    return(data.frame())
  }

  working <- data
  for (col in c(TRUST_QUESTION_KEYS, INTERACTION_QUESTION_KEYS, CONFIDENCE_QUESTION_KEYS)) {
    if (col %in% names(working)) {
      working[[col]] <- suppressWarnings(as.numeric(working[[col]]))
    }
  }

  if (all(c(
    "skeptical_rating",
    "data_trust",
    "usability_difficulty",
    "comprehension_ease"
  ) %in% names(working))) {
    working$skeptical_rating_rev <- 8 - working$skeptical_rating
    working$usability_difficulty_rev <- 8 - working$usability_difficulty
    working$composite_trust_score <- rowMeans(
      working[, c(
        "skeptical_rating_rev",
        "data_trust",
        "usability_difficulty_rev",
        "comprehension_ease"
      ), drop = FALSE],
      na.rm = FALSE
    )
  }

  if (all(INTERACTION_QUESTION_KEYS %in% names(working))) {
    working$composite_interaction_score <- rowMeans(
      working[, INTERACTION_QUESTION_KEYS, drop = FALSE],
      na.rm = FALSE
    )
  }

  if (all(CONFIDENCE_QUESTION_KEYS %in% names(working))) {
    working$confidence_score <- rowMeans(
      working[, CONFIDENCE_QUESTION_KEYS, drop = FALSE],
      na.rm = FALSE
    )
  }

  working
}

classify_interaction_mode <- function(condition_name) {
  name_value <- tolower(as.character(condition_name))

  mode <- ifelse(
    grepl("click", name_value),
    "click",
    ifelse(
      grepl("hover", name_value),
      "hover",
      ifelse(grepl("static", name_value), "static", NA_character_)
    )
  )

  mode
}
```

## Data Loading and Preprocessing (0325 + 0328)

```{r data-loading-and-preprocessing}
csv_manifest <- do.call(
  rbind,
  lapply(existing_data_dirs, function(data_dir) {
    batch_id <- basename(dirname(data_dir))
    files <- sort(list.files(
      data_dir,
      pattern = params$csv_pattern,
      full.names = TRUE
    ))

    if (length(files) == 0) {
      return(data.frame())
    }

    data.frame(
      data_batch = batch_id,
      file_path = files,
      stringsAsFactors = FALSE
    )
  })
)

if (nrow(csv_manifest) == 0) {
  stop("No CSV files found in any required data directory.")
}

all_data <- lapply(seq_len(nrow(csv_manifest)), function(i) {
  file_path <- csv_manifest$file_path[[i]]
  batch_id <- csv_manifest$data_batch[[i]]

  df <- read.csv(file_path, stringsAsFactors = FALSE)
  df$source_file <- basename(file_path)
  df$data_batch <- batch_id

  if (!("participant_id" %in% names(df)) || all(is.na(df$participant_id))) {
    df$participant_id <- extract_participant_id_from_filename(file_path)
  }

  if (!("condition_id" %in% names(df))) {
    df$condition_id <- NA_character_
  }

  if (!("condition_name" %in% names(df))) {
    df$condition_name <- NA_character_
  }

  df$condition_number <- vapply(df$condition_id, extract_condition_number, numeric(1))
  df$condition_label <- map_condition_labels(df$condition_number)
  df
})

combined_data <- bind_rows(all_data)

before_participants <- dplyr::n_distinct(combined_data$participant_id, na.rm = TRUE)
combined_data <- combined_data[!is.na(combined_data$participant_id), , drop = FALSE]
combined_data <- combined_data[
  tolower(as.character(combined_data$participant_id)) != "test",
  ,
  drop = FALSE
]

attention_failures <- identify_attention_check_failures(combined_data)
if (length(attention_failures$ids) > 0) {
  combined_data <- combined_data[
    !(as.character(combined_data$participant_id) %in% attention_failures$ids),
    ,
    drop = FALSE
  ]
}

after_participants <- dplyr::n_distinct(combined_data$participant_id, na.rm = TRUE)

cat("Data directories used:\n")
cat(paste0("- ", existing_data_dirs), sep = "\n")
cat("\nFound CSV files:", nrow(csv_manifest), "\n")
cat("Combined shape:", paste(dim(combined_data), collapse = " x "), "\n")
cat("Participants:", before_participants, "->", after_participants, "\n")
cat("Attention-check exclusions:", length(attention_failures$ids), "\n")
if (length(attention_failures$ids) > 0) {
  cat("Attention-check failure IDs:\n")
  cat(paste0("- ", sort(unique(as.character(attention_failures$ids)))), sep = "\n")
  cat("\n\n")
} else {
  cat("Attention-check failure IDs: none\n\n")
}

batch_counts <- combined_data %>%
  dplyr::filter(trial_type == "trust-survey") %>%
  dplyr::group_by(data_batch) %>%
  dplyr::summarise(
    participants = dplyr::n_distinct(participant_id),
    trust_survey_rows = dplyr::n(),
    .groups = "drop"
  )

cat("Trust-survey counts by batch:\n")
for (i in seq_len(nrow(batch_counts))) {
  cat(
    "-",
    batch_counts$data_batch[[i]],
    ": participants =",
    batch_counts$participants[[i]],
    ", rows =",
    batch_counts$trust_survey_rows[[i]],
    "\n"
  )
}

trust_survey_rows <- combined_data %>%
  dplyr::filter(trial_type == "trust-survey")

trust_survey_expanded <- ensure_likert_columns(
  trust_survey_rows,
  c(TRUST_QUESTION_KEYS, INTERACTION_QUESTION_KEYS)
)

analysis_treatment_survey <- trust_survey_expanded %>%
  dplyr::filter(condition_number %in% TREATMENT_CONDITION_NUMBERS)

prediction_task_rows <- combined_data %>%
  dplyr::filter(trial_type == "prediction-task")

prediction_task_expanded <- ensure_likert_columns(
  prediction_task_rows,
  CONFIDENCE_QUESTION_KEYS
)

confidence_treatment <- prediction_task_expanded %>%
  dplyr::filter(condition_number %in% TREATMENT_CONDITION_NUMBERS) %>%
  dplyr::transmute(
    participant_id = as.character(participant_id),
    condition_number = as.numeric(condition_number),
    confidence_score = suppressWarnings(as.numeric(confidence_rating))
  ) %>%
  dplyr::group_by(participant_id, condition_number) %>%
  dplyr::summarise(
    confidence_score = mean(confidence_score, na.rm = TRUE),
    .groups = "drop"
  )

confidence_treatment$confidence_score[is.nan(confidence_treatment$confidence_score)] <- NA_real_

cat("Trust-survey rows:", nrow(trust_survey_rows), "\n")
cat("Rows with parsed Likert columns:", nrow(trust_survey_expanded), "\n")
cat("Raw treatment trust-survey rows kept:", nrow(analysis_treatment_survey), "\n")
cat("Prediction-task rows:", nrow(prediction_task_rows), "\n")
cat("Raw confidence treatment rows kept:", nrow(confidence_treatment), "\n")
cat(
  "Participants retained in raw treatment trust-survey rows:",
  dplyr::n_distinct(analysis_treatment_survey$participant_id),
  "\n"
)

composite_treatment <- compute_composite_scores(analysis_treatment_survey)
composite_treatment <- composite_treatment %>%
  dplyr::left_join(
    confidence_treatment,
    by = c("participant_id", "condition_number"),
    suffix = c("", "_from_prediction")
  ) %>%
  dplyr::mutate(
    confidence_score = dplyr::coalesce(confidence_score_from_prediction, confidence_score)
  ) %>%
  dplyr::select(-confidence_score_from_prediction)

composite_treatment$condition_label <- map_condition_labels(composite_treatment$condition_number)
composite_treatment$interaction_mode <- classify_interaction_mode(composite_treatment$condition_name)

mode_counts <- composite_treatment %>%
  dplyr::filter(!is.na(interaction_mode)) %>%
  dplyr::group_by(interaction_mode) %>%
  dplyr::summarise(
    participants = dplyr::n_distinct(participant_id),
    rows = dplyr::n(),
    .groups = "drop"
  ) %>%
  dplyr::arrange(interaction_mode)

cat("\nRaw treatment counts by interaction mode:\n")
for (i in seq_len(nrow(mode_counts))) {
  cat(
    "-",
    mode_counts$interaction_mode[[i]],
    ": participants =",
    mode_counts$participants[[i]],
    ", rows =",
    mode_counts$rows[[i]],
    "\n"
  )
}

unknown_mode_rows <- composite_treatment %>%
  dplyr::filter(is.na(interaction_mode))

if (nrow(unknown_mode_rows) > 0) {
  cat("Rows with unknown interaction mode:", nrow(unknown_mode_rows), "\n")
}
```

## Participant-Trajectory Raw Line Plots with Linear Regression by Interaction Mode (9 Plots + 3 Coefficient Tables)

```{r participant-trajectory-raw-linear-by-mode, results='asis', fig.width=9, fig.height=6}
MODE_LEVELS <- c("click", "hover", "static")
MODE_COLORS <- c("click" = "#1f78b4", "hover" = "#33a02c", "static" = "#e15759")

analysis_lines_data <- composite_treatment %>%
  dplyr::filter(
    interaction_mode %in% MODE_LEVELS,
    condition_number %in% TREATMENT_CONDITION_NUMBERS
  ) %>%
  dplyr::mutate(
    participant_id = as.character(participant_id),
    lines = condition_number - 1,
    interaction_mode = factor(interaction_mode, levels = MODE_LEVELS, ordered = TRUE)
  )

if (nrow(analysis_lines_data) == 0) {
  stop("No rows available for linear analyses by interaction mode.")
}

fit_linear_model_by_mode <- function(
  raw_data,
  y_col,
  mode_name
) {
  mode_data <- raw_data %>%
    dplyr::filter(interaction_mode == mode_name, !is.na(.data[[y_col]]))

  if (nrow(mode_data) < 2 || dplyr::n_distinct(mode_data$lines) < 2) {
    stop(
      "Need at least 2 observations and 2 distinct line values for mode: ",
      mode_name,
      " (",
      y_col,
      ")"
    )
  }

  regression_data <- mode_data %>%
    dplyr::transmute(
      participant_id = as.character(participant_id),
      lines = as.numeric(lines),
      y = as.numeric(.data[[y_col]])
    )

  fit <- stats::lm(y ~ lines, data = regression_data)
  coefs <- stats::coef(fit)

  prediction_grid <- data.frame(
    lines = seq(min(regression_data$lines), max(regression_data$lines), length.out = 250)
  )
  prediction_grid$y <- suppressWarnings(as.numeric(stats::predict(fit, newdata = prediction_grid)))

  list(
    fit = fit,
    regression_data = regression_data,
    prediction_data = prediction_grid,
    intercept = unname(coefs[["(Intercept)"]]),
    slope = unname(coefs[["lines"]]),
    n_observations = nrow(regression_data),
    n_participants = dplyr::n_distinct(regression_data$participant_id)
  )
}

format_linear_equation <- function(intercept, slope, digits = 3) {
  sprintf(
    "Linear fit: y = %.*f %s %.*f * lines",
    digits,
    intercept,
    ifelse(slope < 0, "-", "+"),
    digits,
    abs(slope)
  )
}

plot_participant_trajectories_with_fit <- function(
  raw_data,
  mode_fit,
  y_col,
  mode_name,
  title_text,
  y_label_text
) {
  plotting_data <- raw_data %>%
    dplyr::filter(interaction_mode == mode_name, !is.na(.data[[y_col]]))

  ggplot2::ggplot(plotting_data, ggplot2::aes(x = lines, y = .data[[y_col]], group = participant_id)) +
    ggplot2::geom_line(
      color = MODE_COLORS[[mode_name]],
      alpha = 0.22,
      linewidth = 0.55
    ) +
    ggplot2::geom_point(
      color = MODE_COLORS[[mode_name]],
      alpha = 0.45,
      size = 1.9
    ) +
    ggplot2::geom_line(
      data = mode_fit$prediction_data,
      ggplot2::aes(x = lines, y = y),
      color = "#111111",
      linewidth = 1.15,
      inherit.aes = FALSE
    ) +
    ggplot2::scale_x_continuous(breaks = sort(unique(plotting_data$lines))) +
    ggplot2::scale_y_continuous(breaks = seq(1, 7, by = 1)) +
    ggplot2::coord_cartesian(ylim = c(1, 7)) +
    ggplot2::labs(
      title = title_text,
      subtitle = format_linear_equation(mode_fit$intercept, mode_fit$slope),
      x = "Number of Lines",
      y = y_label_text
    ) +
    ggplot2::theme_minimal(base_size = 12) +
    ggplot2::theme(
      plot.background = ggplot2::element_rect(fill = "white", color = NA),
      panel.background = ggplot2::element_rect(fill = "white", color = NA)
    )
}

metric_specs <- list(
  list(
    key = "trust",
    display_name = "Trust",
    y_col = "composite_trust_score",
    y_axis_label = "Trust (raw composite score)"
  ),
  list(
    key = "interaction",
    display_name = "Interactive Experience",
    y_col = "composite_interaction_score",
    y_axis_label = "Interactive Experience (raw composite score)"
  ),
  list(
    key = "confidence",
    display_name = "Confidence",
    y_col = "confidence_score",
    y_axis_label = "Confidence (raw score)"
  )
)

for (metric_spec in metric_specs) {
  available_rows <- analysis_lines_data %>%
    dplyr::filter(!is.na(.data[[metric_spec$y_col]]))

  if (nrow(available_rows) == 0) {
    stop("No rows available for metric: ", metric_spec$display_name)
  }

  cat("### ", metric_spec$display_name, " ~ number of lines (No CI, raw data)\n\n", sep = "")

  mode_fits <- lapply(
    MODE_LEVELS,
    function(mode_name) fit_linear_model_by_mode(analysis_lines_data, metric_spec$y_col, mode_name)
  )
  names(mode_fits) <- MODE_LEVELS

  coefficient_table <- dplyr::bind_rows(
    lapply(MODE_LEVELS, function(mode_name) {
      mode_fit <- mode_fits[[mode_name]]
      data.frame(
        interaction_mode = mode_name,
        intercept = mode_fit$intercept,
        slope = mode_fit$slope,
        observations = mode_fit$n_observations,
        participants = mode_fit$n_participants,
        stringsAsFactors = FALSE
      )
    })
  ) %>%
    dplyr::mutate(
      interaction_mode = factor(interaction_mode, levels = MODE_LEVELS, ordered = TRUE)
    ) %>%
    dplyr::arrange(interaction_mode)

  cat("#### Linear regression coefficients (intercept and slope)\n\n")
  cat(
    as.character(
      knitr::kable(
        coefficient_table,
        format = "html",
        digits = 4,
        col.names = c("Interaction Mode", "Intercept", "Slope", "Observations", "Participants")
      )
    ),
    sep = "\n"
  )
  cat("\n\n")

  for (mode_name in MODE_LEVELS) {
    cat("#### ", metric_spec$display_name, " participant trajectories + linear fit | ", mode_name, "\n\n", sep = "")

    plot_object <- plot_participant_trajectories_with_fit(
      raw_data = analysis_lines_data,
      mode_fit = mode_fits[[mode_name]],
      y_col = metric_spec$y_col,
      mode_name = mode_name,
      title_text = paste0(
        "Experiment 2 (0325 + 0328): ",
        metric_spec$display_name,
        " ~ number of lines (",
        mode_name,
        ")"
      ),
      y_label_text = metric_spec$y_axis_label
    )

    print(plot_object)
    cat("\n")
  }
}
```
