---
title: "Experiment 1 Hypothesis Tests"
output: html_document
params:
  data_dir: "../data/0306/data"
  csv_pattern: "^user_.*\\.csv$"
  alpha: 0.05
  p_adjust_method: "holm"
  seed: 20260321
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(params$seed)
```


## Packages

```{r packages}
required_packages <- c(
  "dplyr",
  "tidyr",
  "ggplot2",
  "jsonlite",
  "knitr",
  "lme4",
  "lmerTest",
  "emmeans"
)

missing_packages <- required_packages[!vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing_packages) > 0) {
  stop(
    "Missing required packages: ",
    paste(missing_packages, collapse = ", "),
    ". Install them before rendering."
  )
}

lapply(required_packages, library, character.only = TRUE)
```

## Paths

```{r paths}
report_dir <- local({
  current_input <- tryCatch(
    knitr::current_input(),
    error = function(e) character(0)
  )

  if (length(current_input) == 1 && nzchar(current_input)) {
    input_path <- current_input
    if (!grepl("^(/|[A-Za-z]:[/\\\\])", input_path)) {
      input_path <- file.path(getwd(), input_path)
    }

    if (grepl("\\.[Rr]md$", input_path) || file.exists(input_path)) {
      return(normalizePath(dirname(input_path), winslash = "/", mustWork = TRUE))
    }
  }

  fallback_dir <- file.path(getwd(), "Experiment1", "analysis")
  normalizePath(fallback_dir, winslash = "/", mustWork = TRUE)
})

resolve_report_path <- function(path_value) {
  if (grepl("^(/|[A-Za-z]:[/\\\\])", path_value)) {
    return(normalizePath(path_value, winslash = "/", mustWork = TRUE))
  }

  normalizePath(
    file.path(report_dir, path_value),
    winslash = "/",
    mustWork = TRUE
  )
}

data_dir <- resolve_report_path(params$data_dir)
```

## Helpers

```{r helpers}
TREATMENT_CONDITIONS <- c(2, 3, 4, 5, 6, 9, 18, 19, 20)

TRUST_ITEM_KEYS <- c(
  "skeptical_rating",
  "data_trust",
  "usability_difficulty",
  "comprehension_ease"
)

INTERACTION_ITEM_KEYS <- c(
  "navigation_control",
  "content_control",
  "pace_control",
  "interface_exploration",
  "interface_responsiveness",
  "user_communication",
  "personal_conversation",
  "interface_interaction",
  "interface_sensitivity"
)

extract_condition_number <- function(condition_id) {
  if (is.na(condition_id) || !nzchar(condition_id)) {
    return(NA_real_)
  }

  parts <- strsplit(as.character(condition_id), "_")[[1]]
  hits <- parts[grepl("^[0-9]+$", parts)]

  if (length(hits) == 0) {
    return(NA_real_)
  }

  as.numeric(hits[[1]])
}

load_participant_data <- function(file_path) {
  df <- read.csv(file_path, stringsAsFactors = FALSE)
  df$source_file <- basename(file_path)

  if (!"participant_id" %in% names(df) || all(is.na(df$participant_id))) {
    participant_id <- strsplit(
      tools::file_path_sans_ext(basename(file_path)),
      "_"
    )[[1]][2]
    df$participant_id <- participant_id
  }

  if ("condition_id" %in% names(df)) {
    df$condition_id[is.na(df$condition_id)] <- "unknown"
    df$condition_number <- vapply(
      df$condition_id,
      extract_condition_number,
      numeric(1)
    )
  } else {
    df$condition_id <- "unknown"
    df$condition_number <- NA_real_
  }

  df
}

parse_response_json <- function(value) {
  if (is.na(value) || !nzchar(value)) {
    return(list())
  }

  parsed <- tryCatch(
    jsonlite::fromJSON(value, simplifyVector = TRUE),
    error = function(e) list()
  )

  if (is.null(parsed) || length(parsed) == 0) {
    return(list())
  }

  parsed
}

expand_response_columns <- function(data) {
  parsed <- lapply(data$response, parse_response_json)
  expanded <- bind_rows(
    lapply(parsed, function(x) {
      if (length(x) == 0) {
        return(data.frame())
      }
      as.data.frame(x, stringsAsFactors = FALSE)
    })
  )

  if (nrow(expanded) == 0) {
    expanded <- data.frame(row.names = seq_len(nrow(data)))
  }

  if (nrow(expanded) < nrow(data)) {
    expanded[(nrow(expanded) + 1):nrow(data), ] <- NA
  }

  overlap <- intersect(names(expanded), names(data))
  if (length(overlap) > 0) {
    data <- data[, setdiff(names(data), overlap), drop = FALSE]
  }

  bind_cols(data, expanded)
}

normalize_likert_0_6_to_1_7 <- function(values) {
  numeric_values <- suppressWarnings(as.numeric(values))
  valid <- numeric_values[!is.na(numeric_values)]

  if (length(valid) == 0) {
    return(numeric_values)
  }

  if (all(valid >= 0 & valid <= 6)) {
    return(pmin(pmax(numeric_values + 1, 1), 7))
  }

  numeric_values
}

reverse_likert_1_7 <- function(values) {
  8 - suppressWarnings(as.numeric(values))
}

map_interaction_group <- function(condition_number) {
  dplyr::case_when(
    condition_number %in% c(2, 3, 9) ~ "Static",
    condition_number %in% c(4, 5, 6) ~ "Interactive",
    condition_number %in% c(18, 19, 20) ~ "Buggy",
    TRUE ~ NA_character_
  )
}

map_vis_type <- function(condition_number) {
  dplyr::case_when(
    condition_number %in% c(2, 5, 19) ~ "PI",
    condition_number %in% c(3, 4, 18) ~ "Ensemble",
    condition_number %in% c(6, 9, 20) ~ "PI + Ensemble",
    TRUE ~ NA_character_
  )
}

safe_min <- function(x) {
  x <- suppressWarnings(as.numeric(x))
  x <- x[is.finite(x)]
  if (length(x) == 0) {
    return(NA_real_)
  }
  min(x)
}

safe_max <- function(x) {
  x <- suppressWarnings(as.numeric(x))
  x <- x[is.finite(x)]
  if (length(x) == 0) {
    return(NA_real_)
  }
  max(x)
}

set_sum_contrasts <- function(data, factors) {
  out <- data
  for (factor_name in factors) {
    out[[factor_name]] <- factor(out[[factor_name]])
    contrasts(out[[factor_name]]) <- contr.sum(length(levels(out[[factor_name]])))
  }
  out
}

augment_contrast_table <- function(table_df, family_label, alpha, adjust_method) {
  out <- as.data.frame(table_df)
  out$family <- family_label
  out$p_adjusted <- p.adjust(out$p.value, method = adjust_method)
  out$alpha <- alpha
  out
}
```

## Load and Prepare Data

```{r load-data}
csv_files <- sort(list.files(
  data_dir,
  pattern = params$csv_pattern,
  full.names = TRUE
))

raw_data <- bind_rows(lapply(csv_files, load_participant_data)) %>%
  filter(!is.na(participant_id)) %>%
  filter(tolower(as.character(participant_id)) != "test")

prediction_rows_raw <- raw_data %>%
  filter(trial_type == "prediction-task")

trust_rows_raw <- raw_data %>%
  filter(trial_type == "trust-survey")

trust_rows_expanded <- expand_response_columns(trust_rows_raw)

for (col in c(TRUST_ITEM_KEYS, INTERACTION_ITEM_KEYS)) {
  if (col %in% names(trust_rows_expanded)) {
    trust_rows_expanded[[col]] <- normalize_likert_0_6_to_1_7(trust_rows_expanded[[col]])
  }
}

trust_treatment <- trust_rows_expanded %>%
  mutate(
    condition_number = suppressWarnings(as.numeric(condition_number)),
    vis_type = map_vis_type(condition_number),
    interaction_group = map_interaction_group(condition_number),
    participant_id = as.character(participant_id)
  ) %>%
  filter(condition_number %in% TREATMENT_CONDITIONS) %>%
  filter(!is.na(vis_type), !is.na(interaction_group))

for (col in c(TRUST_ITEM_KEYS, INTERACTION_ITEM_KEYS)) {
  if (col %in% names(trust_treatment)) {
    trust_treatment[[col]] <- suppressWarnings(as.numeric(trust_treatment[[col]]))
  }
}

trust_treatment <- trust_treatment %>%
  mutate(
    skeptical_rating_scored = reverse_likert_1_7(skeptical_rating),
    usability_difficulty_scored = reverse_likert_1_7(usability_difficulty),
    trust_composite = rowMeans(
      cbind(
        skeptical_rating_scored,
        data_trust,
        usability_difficulty_scored,
        comprehension_ease
      ),
      na.rm = TRUE
    ),
    interaction_composite = rowMeans(
      dplyr::select(., dplyr::all_of(INTERACTION_ITEM_KEYS)),
      na.rm = TRUE
    )
  )

trust_treatment$trust_composite[!is.finite(trust_treatment$trust_composite)] <- NA_real_
trust_treatment$interaction_composite[!is.finite(trust_treatment$interaction_composite)] <- NA_real_

complete_participants <- trust_treatment %>%
  group_by(participant_id) %>%
  summarise(
    n_interaction_groups = n_distinct(interaction_group),
    n_treatment_rows = n(),
    .groups = "drop"
  ) %>%
  filter(n_interaction_groups == 3, n_treatment_rows >= 3) %>%
  pull(participant_id)

h2_data <- trust_treatment %>%
  filter(participant_id %in% complete_participants) %>%
  filter(is.finite(trust_composite)) %>%
  mutate(
    participant_id = factor(participant_id),
    vis_type = factor(vis_type, levels = c("PI", "Ensemble", "PI + Ensemble")),
    interaction_group = factor(interaction_group, levels = c("Static", "Interactive", "Buggy"))
  ) %>%
  droplevels()

h3_data <- trust_treatment %>%
  filter(participant_id %in% complete_participants) %>%
  filter(is.finite(interaction_composite)) %>%
  mutate(
    participant_id = factor(participant_id),
    vis_type = factor(vis_type, levels = c("PI", "Ensemble", "PI + Ensemble")),
    interaction_group = factor(interaction_group, levels = c("Static", "Interactive", "Buggy"))
  ) %>%
  droplevels()

prediction_rows_prepared <- prediction_rows_raw %>%
  mutate(
    phase = suppressWarnings(as.numeric(phase)),
    condition_number = suppressWarnings(as.numeric(condition_number)),
    vis_type = map_vis_type(condition_number),
    interaction_group = map_interaction_group(condition_number),
    confidence_rating = suppressWarnings(as.numeric(confidence_rating)),
    participant_id = as.character(participant_id)
  ) %>%
  filter(is.finite(confidence_rating))

h1_baseline <- prediction_rows_prepared %>%
  filter(phase == 1) %>%
  group_by(participant_id) %>%
  summarise(
    baseline_confidence = mean(confidence_rating, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(is.finite(baseline_confidence))

h1_phase2_condition <- prediction_rows_prepared %>%
  filter(phase %in% c(2, 3, 4)) %>%
  filter(condition_number %in% TREATMENT_CONDITIONS) %>%
  filter(!is.na(vis_type), !is.na(interaction_group), is.finite(condition_number)) %>%
  group_by(participant_id, condition_number, condition_name, vis_type, interaction_group) %>%
  summarise(
    confidence_rating = mean(confidence_rating, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(is.finite(confidence_rating))

h1_data <- h1_phase2_condition %>%
  inner_join(h1_baseline, by = "participant_id") %>%
  mutate(
    confidence_shift = confidence_rating - baseline_confidence,
    participant_id = factor(participant_id),
    vis_type = factor(vis_type, levels = c("PI", "Ensemble", "PI + Ensemble")),
    interaction_group = factor(interaction_group, levels = c("Static", "Interactive", "Buggy"))
  ) %>%
  filter(is.finite(confidence_shift)) %>%
  droplevels()

h1_summary <- h1_data %>%
  group_by(vis_type) %>%
  summarise(
    n = n_distinct(participant_id),
    mean_shift = mean(confidence_shift, na.rm = TRUE),
    sd_shift = sd(confidence_shift, na.rm = TRUE),
    se_shift = sd_shift / sqrt(pmax(n, 1)),
    .groups = "drop"
  ) %>%
  mutate(
    group_category = factor(vis_type, levels = c("PI", "Ensemble", "PI + Ensemble"), ordered = TRUE)
  ) %>%
  arrange(group_category)

h1_data <- h1_data %>%
  mutate(
    vis_type = factor(vis_type, levels = c("PI", "Ensemble", "PI + Ensemble"))
  ) %>%
  droplevels()
```

## Sample Flow and Cell Counts

```{r sample-flow}
sample_flow <- data.frame(
  stage = c(
    "Participant CSV files",
    "Participants after dropping test IDs",
    "Prediction rows (all)",
    "Trust-survey rows (all)",
    "Participants with complete treatment rows (Static + Interactive + Buggy)",
    "H1 rows used",
    "H2 rows used",
    "H3 rows used"
  ),
  value = c(
    length(csv_files),
    dplyr::n_distinct(raw_data$participant_id),
    nrow(prediction_rows_raw),
    nrow(trust_rows_raw),
    length(complete_participants),
    nrow(h1_data),
    nrow(h2_data),
    nrow(h3_data)
  )
)

knitr::kable(sample_flow, align = c("l", "r"))
```

```{r cell-counts}
h1_cell_counts <- h1_data %>%
  count(vis_type, name = "n")

h2_cell_counts <- h2_data %>%
  count(interaction_group, vis_type, name = "n")

knitr::kable(h1_cell_counts, caption = "H1 Cell Counts: Confidence Shift Rows by Visualization Family")
knitr::kable(h2_cell_counts, caption = "H2/H3 Cell Counts: Trust-Survey Rows by Interaction Group and Visualization Family")
```

## Preprocessing Validation

```{r validation-preprocessing}
range_check <- bind_rows(
  data.frame(
    scale = "Trust composite items (normalized)",
    item = TRUST_ITEM_KEYS,
    min_value = vapply(TRUST_ITEM_KEYS, function(k) safe_min(trust_treatment[[k]]), numeric(1)),
    max_value = vapply(TRUST_ITEM_KEYS, function(k) safe_max(trust_treatment[[k]]), numeric(1))
  ),
  data.frame(
    scale = "Interaction composite items (normalized)",
    item = INTERACTION_ITEM_KEYS,
    min_value = vapply(INTERACTION_ITEM_KEYS, function(k) safe_min(trust_treatment[[k]]), numeric(1)),
    max_value = vapply(INTERACTION_ITEM_KEYS, function(k) safe_max(trust_treatment[[k]]), numeric(1))
  )
)

condition_mapping_check <- trust_treatment %>%
  distinct(condition_number, condition_name, interaction_group, vis_type) %>%
  arrange(condition_number)

knitr::kable(range_check, digits = 2, caption = "Likert Range Checks After 0-6 -> 1-7 Normalization")
knitr::kable(condition_mapping_check, caption = "Condition Mapping Check")
```

## H1: Confidence Shift from Baseline by Visualization Family

```{r h1-model}
h1_participant_means <- h1_data %>%
  group_by(participant_id, vis_type) %>%
  summarise(
    baseline_confidence = mean(baseline_confidence, na.rm = TRUE),
    treatment_confidence = mean(confidence_rating, na.rm = TRUE),
    confidence_shift = mean(confidence_shift, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(
    is.finite(baseline_confidence),
    is.finite(treatment_confidence),
    is.finite(confidence_shift)
  )

run_h1_paired_t <- function(df, vis_label, alpha) {
  dat <- df %>%
    filter(vis_type == vis_label)

  if (nrow(dat) < 2) {
    return(data.frame(
      vis_type = vis_label,
      n = nrow(dat),
      mean_baseline = NA_real_,
      mean_treatment = NA_real_,
      mean_diff = NA_real_,
      statistic = NA_real_,
      df = NA_real_,
      p.value = NA_real_,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      stringsAsFactors = FALSE
    ))
  }

  tt <- t.test(
    dat$treatment_confidence,
    dat$baseline_confidence,
    paired = TRUE,
    alternative = "two.sided",
    conf.level = 1 - alpha
  )

  data.frame(
    vis_type = vis_label,
    n = nrow(dat),
    mean_baseline = mean(dat$baseline_confidence, na.rm = TRUE),
    mean_treatment = mean(dat$treatment_confidence, na.rm = TRUE),
    mean_diff = unname(tt$estimate),
    statistic = unname(tt$statistic),
    df = unname(tt$parameter),
    p.value = tt$p.value,
    lower.CL = tt$conf.int[1],
    upper.CL = tt$conf.int[2],
    stringsAsFactors = FALSE
  )
}

h1_vis_levels <- c("PI", "Ensemble", "PI + Ensemble")
h1_paired_table <- bind_rows(
  lapply(h1_vis_levels, function(v) run_h1_paired_t(h1_participant_means, v, params$alpha))
) %>%
  mutate(
    p_adjusted = p.adjust(p.value, method = params$p_adjust_method),
    alpha = params$alpha,
    expected_direction = "Two-sided difference from baseline",
    observed_direction = case_when(
      mean_diff > 0 ~ "Positive",
      mean_diff < 0 ~ "Negative",
      TRUE ~ "Zero"
    )
  )

h1_singular <- NA

knitr::kable(h1_summary, digits = 4, caption = "H1 Summary: Confidence Shift from Baseline by Visualization Family")
knitr::kable(h1_paired_table, digits = 4, caption = "H1 Paired t-tests: Confidence vs Baseline by Visualization Family (Holm-adjusted within H1)")
```

```{r h1-plot, fig.width=7, fig.height=4.5}
h1_plot_data <- h1_summary %>%
  mutate(vis_type = factor(vis_type, levels = c("PI", "Ensemble", "PI + Ensemble"), ordered = TRUE))

ggplot(h1_plot_data, aes(y = vis_type, x = mean_shift)) +
  geom_col(fill = "#9CA3AF", width = 0.72) +
  geom_errorbarh(
    aes(xmin = mean_shift - se_shift, xmax = mean_shift + se_shift),
    height = 0.18,
    color = "#4B5563",
    linewidth = 0.8
  ) +
  geom_vline(xintercept = 0, color = "#6c757d", linetype = "dashed", linewidth = 0.7) +
  scale_x_continuous(limits = c(-1, 1)) +
  labs(
    title = "H1: Confidence Shift from Baseline by Visualization Family (mean +/- SE)",
    x = "Confidence shift from baseline",
    y = "Visualization family"
  ) +
  theme_minimal(base_size = 12) +
  theme(panel.grid = element_blank())
```

## H2: Trust Composite and Interaction Availability by Visualization Family

```{r h2-model}
h2_model_data <- set_sum_contrasts(h2_data, factors = c("interaction_group", "vis_type"))

h2_model <- lmer(
  trust_composite ~ interaction_group * vis_type + (1 | participant_id),
  data = h2_model_data,
  REML = TRUE
)

h2_singular <- lme4::isSingular(h2_model, tol = 1e-5)
h2_anova <- anova(h2_model, type = 3)

h2_emm <- emmeans(h2_model, ~ interaction_group | vis_type)
h2_planned <- contrast(
  h2_emm,
  method = list("Interactive - Static" = c(-1, 1, 0)),
  adjust = "none"
)

h2_planned_table <- augment_contrast_table(
  summary(h2_planned, infer = c(TRUE, TRUE), level = 1 - params$alpha),
  family_label = "H2",
  alpha = params$alpha,
  adjust_method = params$p_adjust_method
) %>%
  mutate(
    planned_test = paste0("Interactive - Static (", vis_type, ")"),
    expected_direction = "Positive estimate supports hypothesis",
    observed_direction = ifelse(estimate > 0, "Positive", "Negative/Zero")
  )

h2_condition_means <- as.data.frame(
  summary(emmeans(h2_model, ~ interaction_group * vis_type), infer = FALSE)
) %>%
  mutate(
    condition = paste(interaction_group, vis_type)
  )

h2_interaction_means <- as.data.frame(
  summary(emmeans(h2_model, ~ interaction_group), infer = FALSE)
)

h2_vis_means <- as.data.frame(
  summary(emmeans(h2_model, ~ vis_type), infer = FALSE)
)

h2_sensitivity <- NULL
h2_sensitivity_table <- NULL
if (h2_singular) {
  h2_sensitivity <- lm(
    trust_composite ~ interaction_group * vis_type + participant_id,
    data = h2_data
  )
  h2_sensitivity_table <- as.data.frame(
    summary(
      contrast(
        emmeans(h2_sensitivity, ~ interaction_group | vis_type),
        method = list("Interactive - Static" = c(-1, 1, 0)),
        adjust = "none"
      ),
      infer = c(TRUE, TRUE),
      level = 1 - params$alpha
    )
  ) %>%
    mutate(
      family = "H2 sensitivity (participant fixed effects)",
      p_adjusted = p.adjust(p.value, method = params$p_adjust_method),
      planned_test = paste0("Interactive - Static (", vis_type, ")")
    )
}

h2_anova
knitr::kable(h2_planned_table, digits = 4, caption = "H2 Planned Contrasts (Holm-adjusted within H2)")
knitr::kable(
  h2_condition_means %>%
    transmute(
      condition,
      interaction_group,
      vis_type,
      mean = emmean,
      se = SE
    ),
  digits = 4,
  caption = "H2 Estimated Means by Individual Condition (Interaction x Visualization)"
)
knitr::kable(
  h2_interaction_means %>%
    transmute(
      interaction_group,
      mean = emmean,
      se = SE
    ),
  digits = 4,
  caption = "H2 Estimated Means by Interaction Group"
)
knitr::kable(
  h2_vis_means %>%
    transmute(
      vis_type,
      mean = emmean,
      se = SE
    ),
  digits = 4,
  caption = "H2 Estimated Means by Visualization Family"
)
if (!is.null(h2_sensitivity_table)) {
  knitr::kable(h2_sensitivity_table, digits = 4, caption = "H2 Sensitivity Contrasts (participant fixed effects)")
}
```

```{r h2-plot, fig.width=8, fig.height=4.8}
h2_plot_data <- h2_condition_means %>%
  mutate(
    ymin = pmax(1, emmean - SE),
    ymax = pmin(7, emmean + SE)
  )

ggplot(h2_plot_data, aes(x = interaction_group, y = emmean, group = 1)) +
  geom_point(size = 2.8, color = "#1B5E20") +
  geom_line(color = "#1B5E20") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.15, color = "#1B5E20") +
  facet_wrap(~ vis_type, nrow = 1) +
  scale_y_continuous(limits = c(1, 7), breaks = 1:7) +
  labs(
    title = "H2: Trust Composite by Interaction Group Within Visualization Family",
    x = "Interaction group",
    y = "Estimated mean trust composite (+/- SE)"
  ) +
  theme_minimal(base_size = 12)
```

## H3: Interaction Experience Composite Across Interaction Availability

```{r h3-model}
h3_model_data <- set_sum_contrasts(h3_data, factors = c("interaction_group", "vis_type"))

h3_model <- lmer(
  interaction_composite ~ interaction_group * vis_type + (1 | participant_id),
  data = h3_model_data,
  REML = TRUE
)

h3_singular <- lme4::isSingular(h3_model, tol = 1e-5)
h3_anova <- anova(h3_model, type = 3)

h3_emm <- emmeans(h3_model, ~ interaction_group)
h3_planned <- contrast(
  h3_emm,
  method = list(
    "Interactive - Buggy" = c(0, 1, -1),
    "Buggy - Static" = c(-1, 0, 1),
    "Interactive - Static" = c(-1, 1, 0)
  ),
  adjust = "none"
)

h3_planned_table <- augment_contrast_table(
  summary(h3_planned, infer = c(TRUE, TRUE), level = 1 - params$alpha),
  family_label = "H3",
  alpha = params$alpha,
  adjust_method = params$p_adjust_method
)

h3_condition_means <- as.data.frame(
  summary(emmeans(h3_model, ~ interaction_group * vis_type), infer = FALSE)
) %>%
  mutate(
    condition = paste(interaction_group, vis_type)
  )

h3_interaction_means <- as.data.frame(
  summary(emmeans(h3_model, ~ interaction_group), infer = FALSE)
)

h3_vis_means <- as.data.frame(
  summary(emmeans(h3_model, ~ vis_type), infer = FALSE)
)

h3_resid_sd <- sigma(h3_model)
h3_planned_table <- h3_planned_table %>%
  mutate(
    std_estimate = estimate / h3_resid_sd,
    std_lower.CL = lower.CL / h3_resid_sd,
    std_upper.CL = upper.CL / h3_resid_sd,
    expected_direction = case_when(
      contrast == "Interactive - Buggy" ~ "Non-negative estimate supports hypothesis",
      contrast == "Buggy - Static" ~ "Positive estimate supports hypothesis",
      contrast == "Interactive - Static" ~ "Positive estimate supports hypothesis",
      TRUE ~ "Directional hypothesis"
    ),
    observed_direction = case_when(
      estimate > 0 ~ "Positive",
      estimate < 0 ~ "Negative",
      TRUE ~ "Zero"
    )
  )

h3_sensitivity <- NULL
h3_sensitivity_table <- NULL
if (h3_singular) {
  h3_sensitivity <- lm(
    interaction_composite ~ interaction_group * vis_type + participant_id,
    data = h3_data
  )
  h3_sensitivity_table <- as.data.frame(
    summary(
      contrast(
        emmeans(h3_sensitivity, ~ interaction_group),
        method = list(
          "Interactive - Buggy" = c(0, 1, -1),
          "Buggy - Static" = c(-1, 0, 1),
          "Interactive - Static" = c(-1, 1, 0)
        ),
        adjust = "none"
      ),
      infer = c(TRUE, TRUE),
      level = 1 - params$alpha
    )
  ) %>%
    mutate(
      family = "H3 sensitivity (participant fixed effects)",
      p_adjusted = p.adjust(p.value, method = params$p_adjust_method)
    )
}

h3_anova
knitr::kable(
  h3_planned_table,
  digits = 4,
  caption = "H3 Planned Contrasts with Approximate Standardized Effects (Holm-adjusted within H3)"
)
knitr::kable(
  h3_condition_means %>%
    transmute(
      condition,
      interaction_group,
      vis_type,
      mean = emmean,
      se = SE
    ),
  digits = 4,
  caption = "H3 Estimated Means by Individual Condition (Interaction x Visualization)"
)
knitr::kable(
  h3_interaction_means %>%
    transmute(
      interaction_group,
      mean = emmean,
      se = SE
    ),
  digits = 4,
  caption = "H3 Estimated Means by Interaction Group"
)
knitr::kable(
  h3_vis_means %>%
    transmute(
      vis_type,
      mean = emmean,
      se = SE
    ),
  digits = 4,
  caption = "H3 Estimated Means by Visualization Family"
)
if (!is.null(h3_sensitivity_table)) {
  knitr::kable(h3_sensitivity_table, digits = 4, caption = "H3 Sensitivity Contrasts (participant fixed effects)")
}
```

```{r h3-plot, fig.width=7, fig.height=4.5}
h3_plot_data <- h3_interaction_means %>%
  mutate(
    ymin = pmax(1, emmean - SE),
    ymax = pmin(7, emmean + SE)
  )

ggplot(h3_plot_data, aes(x = interaction_group, y = emmean)) +
  geom_point(size = 3, color = "#4A148C") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.15, color = "#4A148C") +
  scale_y_continuous(limits = c(1, 7), breaks = 1:7) +
  labs(
    title = "H3: Interaction Experience Composite by Interaction Group",
    x = "Interaction group",
    y = "Estimated mean interaction composite (+/- SE)"
  ) +
  theme_minimal(base_size = 12)
```

## Model Execution Checks

```{r model-checks}
model_checks <- data.frame(
  hypothesis = c("H1", "H2", "H3"),
  rows_used = c(nrow(h1_data), nrow(h2_data), nrow(h3_data)),
  participants = c(
    dplyr::n_distinct(h1_data$participant_id),
    dplyr::n_distinct(h2_data$participant_id),
    dplyr::n_distinct(h3_data$participant_id)
  ),
  vis_levels_present = c(
    all(c("PI", "Ensemble", "PI + Ensemble") %in% levels(h1_data$vis_type)),
    all(c("PI", "Ensemble", "PI + Ensemble") %in% levels(h2_data$vis_type)),
    all(c("PI", "Ensemble", "PI + Ensemble") %in% levels(h3_data$vis_type))
  ),
  interaction_levels_present = c(
    all(c("Static", "Interactive", "Buggy") %in% levels(h1_data$interaction_group)),
    all(c("Static", "Interactive", "Buggy") %in% levels(h2_data$interaction_group)),
    all(c("Static", "Interactive", "Buggy") %in% levels(h3_data$interaction_group))
  ),
  singular_lmm = c(h1_singular, h2_singular, h3_singular)
)

knitr::kable(model_checks, caption = "Model Execution Validation")
```

## Additional ANOVA: Visualization Family Within Interactive Availability Only

```{r interactive-only-vis-anova}
interactive_vis_data <- h2_data %>%
  filter(interaction_group == "Interactive") %>%
  mutate(
    vis_type = factor(vis_type, levels = c("PI", "Ensemble", "PI + Ensemble"))
  ) %>%
  droplevels()

if (nrow(interactive_vis_data) == 0) {
  stop("No rows found for interaction_group == 'Interactive'.")
}

interactive_vis_model <- lm(trust_composite ~ vis_type, data = interactive_vis_data)
interactive_vis_anova <- anova(interactive_vis_model)

interactive_vis_summary <- interactive_vis_data %>%
  group_by(vis_type) %>%
  summarise(
    n = n(),
    mean = mean(trust_composite, na.rm = TRUE),
    sd = sd(trust_composite, na.rm = TRUE),
    se = sd / sqrt(pmax(n, 1)),
    .groups = "drop"
  )

interactive_vis_anova
knitr::kable(
  interactive_vis_summary,
  digits = 4,
  caption = "Interactive-only Trust Composite by Visualization Family"
)
```
