---
title: "Composite Trust Regression and Power Analysis"
output:
  html_document: default
  pdf_document: default
params:
  data_dir: "../data/0306/data"
  csv_pattern: "^user_.*\\.csv$"
  alpha: 0.05
  power_target: 0.8
  power_nsim: 100
  power_cores: 8
  power_grid: [30, 45, 60, 75, 90, 120, 150, 200, 250, 300, 350, 375, 400, 425, 450]
  seed: 20260307
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

```{r table-spacing-style, results='asis', echo=FALSE}
table_column_padding_html <- "2rem"
table_column_padding_latex <- "10pt"

if (knitr::is_html_output()) {
  cat(
    "<style>\n",
    "table th,\n",
    "table td {\n",
    "  padding-left: ", table_column_padding_html, " !important;\n",
    "  padding-right: ", table_column_padding_html, " !important;\n",
    "}\n",
    "</style>\n",
    sep = ""
  )
}

if (knitr::is_latex_output()) {
  cat("\\setlength{\\tabcolsep}{", table_column_padding_latex, "}\n", sep = "")
}
```

## Goal

This report follows the preprocessing used in `analysis-0306.ipynb`, excludes the baseline condition, and analyzes:

`composite_trust ~ interaction_availability + vis_type`

Because each participant contributes three non-baseline trust responses, the regression is fit as a mixed-effects model with a participant random intercept:

`composite_trust ~ interaction_availability + vis_type + (1 | participant_id)`

The power analysis below uses the fitted pilot model and the observed three-row-per-participant design templates to estimate how many participants are needed for statistically significant main effects.

## Packages

```{r packages}
library(dplyr)
library(ggplot2)
library(jsonlite)
library(knitr)
library(lme4)
library(lmerTest)
```

## Paths

```{r paths}
report_dir <- local({
  current_input <- tryCatch(
    knitr::current_input(),
    error = function(e) character(0)
  )

  if (length(current_input) == 1 && nzchar(current_input)) {
    input_path <- current_input

    if (!grepl("^(/|[A-Za-z]:[/\\\\])", input_path)) {
      input_path <- file.path(getwd(), input_path)
    }

    if (grepl("\\.[Rr]md$", input_path) || file.exists(input_path)) {
      return(normalizePath(dirname(input_path), winslash = "/", mustWork = TRUE))
    }
  }

  current_input_dir <- tryCatch(
    knitr::current_input(dir = TRUE),
    error = function(e) character(0)
  )

  if (length(current_input_dir) == 1 && nzchar(current_input_dir)) {
    if (grepl("\\.[Rr]md$", current_input_dir)) {
      return(normalizePath(dirname(current_input_dir), winslash = "/", mustWork = TRUE))
    }

    if (dir.exists(current_input_dir)) {
      return(normalizePath(current_input_dir, winslash = "/", mustWork = TRUE))
    }
  }

  fallback_dir <- file.path(getwd(), "Experiment1", "analysis")
  normalizePath(fallback_dir, winslash = "/", mustWork = TRUE)
})

resolve_report_path <- function(path_value) {
  if (grepl("^(/|[A-Za-z]:[/\\\\])", path_value)) {
    return(normalizePath(path_value, winslash = "/", mustWork = TRUE))
  }

  normalizePath(
    file.path(report_dir, path_value),
    winslash = "/",
    mustWork = TRUE
  )
}

data_dir <- resolve_report_path(params$data_dir)
```

## Helper Functions

```{r helpers}
extract_condition_number <- function(condition_id) {
  if (is.na(condition_id) || !nzchar(condition_id)) {
    return(NA_real_)
  }

  parts <- strsplit(as.character(condition_id), "_")[[1]]
  hits <- parts[grepl("^[0-9]+$", parts)]

  if (length(hits) == 0) {
    return(NA_real_)
  }

  as.numeric(hits[[1]])
}

load_participant_data <- function(file_path) {
  df <- read.csv(file_path, stringsAsFactors = FALSE)
  df$source_file <- basename(file_path)

  if (!"participant_id" %in% names(df) || all(is.na(df$participant_id))) {
    participant_id <- strsplit(
      tools::file_path_sans_ext(basename(file_path)),
      "_"
    )[[1]][2]
    df$participant_id <- participant_id
  }

  if ("condition_id" %in% names(df)) {
    df$condition_id[is.na(df$condition_id)] <- "unknown"
    df$condition_number <- vapply(
      df$condition_id,
      extract_condition_number,
      numeric(1)
    )
  } else {
    df$condition_id <- "unknown"
    df$condition_number <- NA_real_
  }

  df
}

parse_response_json <- function(value) {
  if (is.na(value) || !nzchar(value)) {
    return(list())
  }

  parsed <- tryCatch(
    fromJSON(value, simplifyVector = TRUE),
    error = function(e) list()
  )

  if (is.null(parsed)) {
    return(list())
  }

  parsed
}

expand_response_columns <- function(data) {
  parsed <- lapply(data$response, parse_response_json)
  expanded <- bind_rows(
    lapply(parsed, function(x) {
      if (length(x) == 0) {
        return(data.frame())
      }

      as.data.frame(x, stringsAsFactors = FALSE)
    })
  )

  if (nrow(expanded) == 0) {
    expanded <- data.frame(row.names = seq_len(nrow(data)))
  }

  if (nrow(expanded) < nrow(data)) {
    expanded[(nrow(expanded) + 1):nrow(data), ] <- NA
  }

  overlap <- intersect(names(expanded), names(data))
  if (length(overlap) > 0) {
    data <- data[, setdiff(names(data), overlap), drop = FALSE]
  }

  bind_cols(data, expanded)
}

normalize_likert_0_6_to_1_7 <- function(values) {
  numeric_values <- suppressWarnings(as.numeric(values))
  valid <- numeric_values[!is.na(numeric_values)]

  if (length(valid) == 0) {
    return(numeric_values)
  }

  if (all(valid >= 0 & valid <= 6)) {
    return(pmin(pmax(numeric_values + 1, 1), 7))
  }

  numeric_values
}

reverse_likert_1_7 <- function(values) {
  8 - suppressWarnings(as.numeric(values))
}

map_interaction_availability <- function(condition_number) {
  dplyr::case_when(
    condition_number %in% c(2, 3, 9) ~ "static",
    condition_number %in% c(4, 5, 6) ~ "interactive",
    condition_number %in% c(18, 19, 20) ~ "buggy",
    TRUE ~ NA_character_
  )
}

map_vis_type <- function(condition_number) {
  dplyr::case_when(
    condition_number %in% c(2, 5, 19) ~ "CI",
    condition_number %in% c(3, 4, 18) ~ "Ensemble",
    condition_number %in% c(6, 9, 20) ~ "Combined",
    TRUE ~ NA_character_
  )
}

fit_trust_model <- function(data, reml = TRUE) {
  contrasts(data$interaction_availability) <- contr.sum(3)
  contrasts(data$vis_type) <- contr.sum(3)

  lmer(
    composite_trust ~ interaction_availability + vis_type + (1 | participant_id),
    data = data,
    REML = reml
  )
}

build_power_context <- function(pilot_data, pilot_model) {
  participant_templates <- pilot_data %>%
    group_by(participant_id) %>%
    summarise(
      interaction_levels = list(as.character(interaction_availability)),
      vis_levels = list(as.character(vis_type)),
      .groups = "drop"
    )

  vc <- as.data.frame(VarCorr(pilot_model))
  list(
    participant_templates = participant_templates,
    participant_sd = vc$sdcor[vc$grp == "participant_id"][1],
    residual_sd = sigma(pilot_model),
    fixed_effects = fixef(pilot_model),
    interaction_levels = levels(pilot_data$interaction_availability),
    vis_levels = levels(pilot_data$vis_type)
  )
}

simulate_dataset_from_context <- function(n_participants, power_context) {
  template_idx <- sample(
    seq_len(nrow(power_context$participant_templates)),
    size = n_participants,
    replace = TRUE
  )

  simulated_rows <- vector("list", n_participants)

  for (i in seq_len(n_participants)) {
    design <- data.frame(
      participant_id = factor(paste0("sim_", i)),
      interaction_availability = factor(
        power_context$participant_templates$interaction_levels[[template_idx[i]]],
        levels = power_context$interaction_levels
      ),
      vis_type = factor(
        power_context$participant_templates$vis_levels[[template_idx[i]]],
        levels = power_context$vis_levels
      )
    )

    contrasts(design$interaction_availability) <- contr.sum(3)
    contrasts(design$vis_type) <- contr.sum(3)

    subject_effect <- rnorm(1, mean = 0, sd = power_context$participant_sd)
    mu <- as.numeric(
      model.matrix(~ interaction_availability + vis_type, design) %*% power_context$fixed_effects
    )

    design$composite_trust <- rnorm(
      n = nrow(design),
      mean = mu + subject_effect,
      sd = power_context$residual_sd
    )

    simulated_rows[[i]] <- design
  }

  bind_rows(simulated_rows)
}

estimate_power <- function(n_participants, power_context, alpha = 0.05, nsim = 40) {
  hits_interaction <- logical(nsim)
  hits_vis <- logical(nsim)

  for (sim_idx in seq_len(nsim)) {
    sim_data <- simulate_dataset_from_context(
      n_participants = n_participants,
      power_context = power_context
    )

    sim_fit <- suppressWarnings(fit_trust_model(sim_data, reml = FALSE))
    sim_anova <- suppressMessages(anova(sim_fit, type = 3))
    row_names <- rownames(sim_anova)

    p_interaction <- sim_anova[
      grep("^interaction_availability$", row_names),
      "Pr(>F)"
    ]
    p_vis <- sim_anova[
      grep("^vis_type$", row_names),
      "Pr(>F)"
    ]

    hits_interaction[sim_idx] <- length(p_interaction) == 1 && !is.na(p_interaction) && p_interaction < alpha
    hits_vis[sim_idx] <- length(p_vis) == 1 && !is.na(p_vis) && p_vis < alpha
  }

  data.frame(
    n_participants = n_participants,
    power_interaction = mean(hits_interaction),
    power_vis_type = mean(hits_vis),
    power_both = mean(hits_interaction & hits_vis)
  )
}

first_n_at_target <- function(power_table, column_name, target) {
  hits <- power_table[power_table[[column_name]] >= target, "n_participants", drop = TRUE]
  if (length(hits) == 0) {
    return(NA_real_)
  }
  min(hits)
}
```

## Load the 0306 Data

```{r load-data}
csv_files <- sort(list.files(
  data_dir,
  pattern = params$csv_pattern,
  full.names = TRUE
))

raw_data <- bind_rows(lapply(csv_files, load_participant_data)) %>%
  filter(!is.na(participant_id)) %>%
  filter(tolower(as.character(participant_id)) != "test")

relevant_trial_types <- c(
  "prediction-task",
  "vis-literacy",
  "trust-survey",
  "personality-survey",
  "survey-multi-choice",
  "survey-text",
  "interaction-feedback"
)

relevant_trials <- raw_data %>%
  filter(trial_type %in% relevant_trial_types) %>%
  mutate(
    interaction_freq = log1p(
      nchar(ifelse(is.na(interaction_log), "", as.character(interaction_log)))
    )
  )

trust_survey_rows <- relevant_trials %>%
  filter(trial_type == "trust-survey")

trust_survey_expanded <- expand_response_columns(trust_survey_rows)

trust_question_keys <- c(
  "skeptical_rating",
  "data_trust",
  "usability_difficulty",
  "comprehension_ease"
)

for (col in trust_question_keys) {
  if (col %in% names(trust_survey_expanded)) {
    trust_survey_expanded[[col]] <- normalize_likert_0_6_to_1_7(
      trust_survey_expanded[[col]]
    )
  }
}
```

## Build the Analysis Dataset

This keeps only the nine treatment conditions and excludes baseline (`condition_1_baseline`).

```{r analysis-data}
analysis_data <- trust_survey_expanded %>%
  filter(!is.na(skeptical_rating)) %>%
  mutate(
    condition_number = suppressWarnings(as.numeric(condition_number)),
    interaction_availability = map_interaction_availability(condition_number),
    vis_type = map_vis_type(condition_number),
    skeptical_rating_scored = reverse_likert_1_7(skeptical_rating),
    data_trust_scored = suppressWarnings(as.numeric(data_trust)),
    usability_difficulty_scored = reverse_likert_1_7(usability_difficulty),
    comprehension_ease_scored = suppressWarnings(as.numeric(comprehension_ease)),
    composite_trust = rowMeans(
      cbind(
        skeptical_rating_scored,
        data_trust_scored,
        usability_difficulty_scored,
        comprehension_ease_scored
      ),
      na.rm = TRUE
    )
  ) %>%
  filter(!is.na(interaction_availability)) %>%
  filter(!is.na(vis_type)) %>%
  filter(is.finite(composite_trust)) %>%
  mutate(
    interaction_availability = factor(
      interaction_availability,
      levels = c("static", "interactive", "buggy")
    ),
    vis_type = factor(
      vis_type,
      levels = c("CI", "Ensemble", "Combined")
    ),
    participant_id = factor(participant_id)
  ) %>%
  group_by(participant_id, interaction_availability, vis_type) %>%
  summarise(
    composite_trust = mean(composite_trust),
    .groups = "drop"
  )

participant_row_counts <- analysis_data %>%
  count(participant_id, name = "treatment_rows")

complete_participants <- participant_row_counts %>%
  filter(treatment_rows == 3) %>%
  pull(participant_id)

analysis_data <- analysis_data %>%
  filter(participant_id %in% complete_participants) %>%
  droplevels()

analysis_overview <- data.frame(
  metric = c(
    "Participant CSV files",
    "Participants after dropping test IDs",
    "Trust-survey rows",
    "Participants in final treatment dataset",
    "Treatment observations in final dataset"
  ),
  value = c(
    length(csv_files),
    dplyr::n_distinct(raw_data$participant_id),
    nrow(trust_survey_rows),
    dplyr::n_distinct(analysis_data$participant_id),
    nrow(analysis_data)
  )
)

kable(analysis_overview, align = c("l", "r"))
```

### Cell Counts

```{r cell-counts}
cell_counts <- analysis_data %>%
  count(interaction_availability, vis_type, name = "n")

kable(cell_counts)
```

### Factor Means

```{r factor-means}
interaction_summary <- analysis_data %>%
  group_by(interaction_availability) %>%
  summarise(
    participants = n_distinct(participant_id),
    rows = n(),
    mean_composite_trust = mean(composite_trust),
    sd_composite_trust = sd(composite_trust),
    .groups = "drop"
  )

vis_summary <- analysis_data %>%
  group_by(vis_type) %>%
  summarise(
    participants = n_distinct(participant_id),
    rows = n(),
    mean_composite_trust = mean(composite_trust),
    sd_composite_trust = sd(composite_trust),
    .groups = "drop"
  )

kable(interaction_summary, digits = 3)
kable(vis_summary, digits = 3)
```

## Regression

```{r model-fit}
trust_model <- fit_trust_model(analysis_data, reml = TRUE)

model_summary <- summary(trust_model)
anova_summary <- anova(trust_model, type = 3)

model_summary
anova_summary
```

```{r observed-plot, fig.width=8, fig.height=5}
ggplot(
  analysis_data,
  aes(x = vis_type, y = composite_trust, color = interaction_availability)
) +
  stat_summary(fun = mean, geom = "point", size = 3, position = position_dodge(width = 0.2)) +
  stat_summary(
    fun.data = mean_se,
    geom = "errorbar",
    width = 0.15,
    position = position_dodge(width = 0.2)
  ) +
  labs(
    title = "Composite Trust by Interaction Availability and Visualization Type",
    x = "Visualization type",
    y = "Composite trust score",
    color = "Interaction availability"
  ) +
  theme_minimal(base_size = 12)
```

## Power Analysis

The simulation below uses the fitted pilot model, the observed participant-level three-row treatment design, and `r params$power_nsim` simulated datasets per candidate sample size.

```{r power-analysis}
set.seed(params$seed)

power_context <- build_power_context(analysis_data, trust_model)

power_runner <- function(n_value) {
  estimate_power(
    n_participants = n_value,
    power_context = power_context,
    alpha = params$alpha,
    nsim = params$power_nsim
  )
}

power_results <- if (.Platform$OS.type != "windows" && params$power_cores > 1) {
  bind_rows(
    parallel::mclapply(
      params$power_grid,
      power_runner,
      mc.cores = params$power_cores,
      mc.set.seed = TRUE
    )
  )
} else {
  bind_rows(lapply(params$power_grid, power_runner))
}

power_results <- power_results %>%
  arrange(n_participants)

recommended_n_interaction <- first_n_at_target(
  power_results,
  "power_interaction",
  params$power_target
)
recommended_n_vis <- first_n_at_target(
  power_results,
  "power_vis_type",
  params$power_target
)
recommended_n_both <- first_n_at_target(
  power_results,
  "power_both",
  params$power_target
)

kable(power_results, digits = 3)
```

```{r power-plot, fig.width=8, fig.height=5}
power_long <- bind_rows(
  data.frame(
    n_participants = power_results$n_participants,
    outcome = "interaction_availability",
    power = power_results$power_interaction
  ),
  data.frame(
    n_participants = power_results$n_participants,
    outcome = "vis_type",
    power = power_results$power_vis_type
  ),
  data.frame(
    n_participants = power_results$n_participants,
    outcome = "both main effects",
    power = power_results$power_both
  )
)

ggplot(power_long, aes(x = n_participants, y = power, color = outcome)) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 2) +
  geom_hline(
    yintercept = params$power_target,
    linetype = "dashed",
    color = "gray45"
  ) +
  scale_y_continuous(limits = c(0, 1)) +
  labs(
    title = "Simulation-Based Power Curve",
    x = "Participants",
    y = "Estimated power",
    color = "Target"
  ) +
  theme_minimal(base_size = 12)
```
